---
title: "Pre-scenario coding"
author: "Dorit Stein"
date: "1/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(readxl)
library(astsa)
library(fuzzyjoin)
library(plm)
library(tidyverse)
library(purrr)
library(knitr)
library(haven)
library(srvyr)
library(survey)
library(vroom)
library(data.table)
library(janitor)
library(qdapRegex)

library(globorisk)


```

1. Load cleaned data

```{r data}

data <- read_csv("1 Raw Data/cleaned_final.csv") # August 31, 2022

```

2. Select countries for analytical sample and clean other variables
 - unique PSUs
 - check missingness: Select countries for analysis with <35.5% missingness for wealth_quintile variable
    (other high missing countries were already filtered out in data cleaning)
 - drop missing wealth_quintile individuals (now have complete.case dataset)
 - filter out implausible sbp values
 - fix countryGDPclass

```{r analytical sample}

# Make sure psu_num really is unique within each country
data <- data %>% 
  mutate(psu_num = str_c(Country, psu, sep = "_"),
         stratum_num = stratum)

# drop countries with > 0.355 missingness for wealth_quintile
# pct_na_wealth
data2 <- data %>%
  filter(pct_na_wealth < 0.355)

# countries to include - 52 total
countries <- unique(data2$Country)

# clean year
# drop missing wealth_quintile individuals (complete.cases dataset now)
# filter out implausible sbp
data3 <- data2 %>%
  drop_na(wealth_quintile) %>% 
  mutate(year = ifelse(year == "2015-2016", "2015",
                ifelse(year == "2009-10", "2009",
                ifelse(year == "2009-11", "2010", 
                ifelse(year == "2009-12", "2011",
                ifelse(year == "2014-15", "2014",
                ifelse(year == "2005-6", "2005",
                ifelse(year == "2007/8", "2007", year)))))))) %>%
  rowid_to_column("ID") %>%
  mutate(Country = case_when(Country == "Swaziland" ~ "Eswatini",
                             TRUE ~ Country)) %>%
  filter(sbp <= 270 & sbp >= 70) %>%
  mutate(countryGDPclass = case_when(countryGDPclass == "Low Income Country" ~ "1",
                                     countryGDPclass == "Lower-middle Income Country" ~ "2",
                                     countryGDPclass == "Upper-middle Income Country" ~ "3",
                                     TRUE ~ countryGDPclass))

data3$countryGDPclass <- factor(data3$countryGDPclass,
                            levels = c("1","2", "3"),
                            labels = c("Low-income", "Lower-middle Income", "Upper-middle Income"))
data3$wealth_quintile2 <- factor(data3$wealth_quintile,
                                     levels = c("1", "2", "3", "4", "5"),
                                     labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))

# Aug 29, 2022 (with htn/non-htns, complete.cases for relevant variables)
saveRDS(data3, "3 Output/data.rds") 

```

3. Hypertension prevalence estimates (country, country-quintile level)
 - using analytical sample with complete.cases for relevant variables
 - by country, and by country-quintile
 
```{r htn prevalence}

data3 <- readRDS("3 Output/data.rds")

# set survey design for hypertension prevalence estimates by country, and country-quintile
data_htn <- data3 %>%
  as_survey_design(
    stratum = stratum_num,
    ids = c(psu_num),
    weights = w_bp)

##weighted mean of hypertensives by country and country-quintile

# by country
htn <- data_htn %>%
  group_by(Country) %>%
  summarize(mean_htn = survey_mean(clin_hypt, vartype = "ci"))

# save
saveRDS(htn, file ="3 Output/htn-country.rds")

# by country-quintile
htn_quintile <- data_htn %>%
  group_by(Country, wealth_quintile) %>%
  summarize(
    mean_htn = survey_mean(clin_hypt, vartype = "ci"))

# save
saveRDS(htn_quintile, file ="3 Output/htn-quintile.rds")

# merge in htn prevalence data to main dataset
data4 <- data3 %>%
  left_join(htn)

saveRDS(data4, "3 Output/data4.rds")

```

4. Weights for RRs from GBD (country/sex/age-group)
 - get country/sex/age-group proportions of deaths from IHD vs CHD to weight RRs by, from GBD

```{r GBD rr weights}

# load GBD data
# Accessed Monday January 10th 2022

gbd <- read.csv("1 Raw Data/IHMD-GBD-CVD-Data-Jan.10.2022/IHME-GBD_2019_DATA-8de51a8d-1.csv")

head(gbd)

countries_gbd <- unique(gbd$location_name)

measures <- unique(gbd$measure_name)

causes <- unique(gbd$cause_name)

cause_id <- unique(gbd$cause_id)

# measures - incidence and death
# metrics - number or percent
# cause_name - 
#[1] "Cardiovascular diseases"              "Rheumatic heart disease"              "Ischemic heart disease"              
#[4] "Stroke"                               "Non-rheumatic valvular heart disease" "Cardiomyopathy and myocarditis"      
#[7] "Hypertensive heart disease" 
# cause_id - want 
# stroke - 494
# IHD - 493

# get total sum of IHD and stroke deaths/incidence
# get proportion IHD and stroke represent of total for each country-age-sex grouping
gbd2 <- gbd %>%
  filter(cause_id == 493 | cause_id == 494) %>%
  filter(metric_name == "Number") %>%
  filter(measure_name == "Deaths") %>%
  filter(sex_id != 3) %>%
  mutate(Country = location_name) %>%
  group_by(Country, measure_name, sex_id, sex_name, age_id, age_name) %>%
  mutate(total = sum(val)) %>%
  ungroup() %>%
  mutate(prop = val/total) %>%
  group_by(Country, measure_name, sex_id, sex_name, age_id, age_name) %>%
  mutate(sum_w = sum(prop)) %>%
  ungroup()

# pull out country names
countries <- c(unique(data3$Country))

# filter countries to get ratios of stroke vs IHD
# make uppercase, rename some to match

gbd3 <- gbd2 %>%
  mutate(Country = case_when(Country == "Lao People's Democratic Republic" ~ "Laos",
                             Country == "Iran (Islamic Republic of)" ~ "Iran",
                             Country == "Republic of Moldova" ~ "Moldova",
                             Country == "Saint Vincent and the Grenadines" ~ "St. Vincent & the Grenadines",
                             Country == "United Republic of Tanzania" ~ "Tanzania",
                             Country == "Timor-Leste" ~ "Timor Leste",
                                  TRUE ~ Country),
         sex = case_when(sex_id == 1 ~ 0,
                         sex_id == 2 ~ 1,
                         TRUE ~ NA_real_)) %>%
  filter(Country %in% countries) %>%
  select(sex, age_id, age_name, cause_name, -year, Country, prop) %>%
  pivot_wider(values_from = prop, names_from = cause_name) %>%
  rename(prop_ihd = "Ischemic heart disease",
         prop_stroke = "Stroke")

# see which countries matched in population dataset
matched <- sort(c(unique(gbd3$Country)))

# countries that did not match
missing <- setdiff(countries, matched)
#> missing
#[1] "Gambia" Gambia                      
# "Iran" Iran (Islamic Republic of)                        
# "Laos"    Lao People's Democratic Republic                    
#[4] "Moldova"            Republic of Moldova
#"St. Vincent & the Grenadines" 
#"Swaziland"  "Eswatini"                 
#[7] "Tanzania"   United Republic of Tanzania
#"Timor Leste"   Timor-Leste

# save country-level RRs
saveRDS(gbd3, file = "3 Output/gbd-chd-stroke.rds")

```

5. Calculate individual RRs (individual-level data)
 - using Law et al equations
 - using GBD weights from chunk above

```{r RR calculations}

data4 <- readRDS("3 Output/data4.rds")

# calculate sbp change due to one med at standard dose from Law et al equation
  # create 5 year age groups with same labels as GBD 5-year age groups to merge in CHD and Stroke proportion data
  # assign RR for CHD and Stroke depending on 10 year age group from Law et al paper
  # merge in country proportions
  # generate weighted RR for each person if they were to be put on treatment (and apply to their CVD risk score later)

data_sbp <- data4 %>%
  mutate(sex = as.numeric(sex),
         sbp_change = 9+(0.10*(sbp-154)),
         age_id = case_when(age >=40 & age<45 ~ 13,
                              age >=45 & age<50 ~ 14, 
                              age >=50 & age<55 ~ 15, 
                              age>=55 & age<60 ~ 16,
                              age>=60 & age<65 ~ 17,
                              age>=65 & age<70 ~ 18,
                              age>=70 & age<75 ~ 19,
                              age>=75 & age<80 ~ 20,
                              age>=80 & age<85 ~ 30,
                              age>=85 & age <90 ~ 31,
                           TRUE ~ NA_real_),
         rr_chd = case_when(age_id == 13 | age_id == 14 ~ 0.49,
                            age_id == 15 | age_id == 16 ~ 0.5,
                            age_id == 17 | age_id == 18 ~ 0.54,
                            age_id == 19 | age_id == 20 ~ 0.6,
                            age_id == 30 | age_id == 31 ~ 0.67,
                                        TRUE ~ NA_real_),
         rr_stroke = case_when(age_id == 13 | age_id == 14 ~ 0.36,
                               age_id == 15 | age_id == 16 ~ 0.38,
                               age_id == 17 | age_id == 18 ~ 0.43,
                               age_id == 19 | age_id == 20 ~ 0.5,
                               age_id == 30 | age_id == 31 ~ 0.67,
                                        TRUE ~ NA_real_),
         rr_chd_adj = rr_chd^(sbp_change/20),
         rr_stroke_adj = rr_stroke^(sbp_change/20)) 

# load GBD data for proportions of deaths due to CHD and Stroke for each country-sex-age group
# from chunk above
gbd3 <- readRDS(file = "3 Output/gbd-chd-stroke.rds")

data_gbd <- data_sbp %>% 
  left_join(gbd3)

# calculate composite adjusted RR for each person
data_cvd_rr <- data_gbd %>%
  mutate(rr_w = (rr_chd_adj*prop_ihd)+(rr_stroke_adj*prop_stroke),
         cvd_reduction = rr_w)

# save
saveRDS(data_cvd_rr, file = "3 Output/all-w-RRs.rds")

```

6. Globorisk
 - individual CVD risk calculations

```{r globorisk}

data_cvd_rr <- readRDS("3 Output/all-w-RRs.rds")

#run dataset into globorisk to get 10-year CVD risk for each person (line) in the dataset
data_cvd <- data_cvd_rr %>%
  mutate(cvd_risk = globorisk::globorisk(
  sex = sex,
  age = age,
  sbp = sbp,
  smk = csmoke,
  bmi = bmi,
  iso = ccodes,
  year = year, 
  version = "office",
  type = "risk")
) 

#save 
saveRDS(data_cvd, file= "3 Output/analysis-w-cvd.rds")

```

# AMONG HYPERTENSIVES ONLY

7. Cascade performance summary 
 - summarize cascade for each country-quintile
 - select "best performers" at each step (create column in dataset with best performer value?)
 - AUC gap calculations

```{r cascades}

data_cvd <- readRDS(file= "3 Output/analysis-w-cvd.rds") %>%
  filter(clin_hypt == 1)

saveRDS(data_cvd, "3 Output/all-w-RRs.rds") # use this in next chunk

gdp <- data_cvd %>%
  group_by(Country) %>%
  summarize(countryGDPclass = unique(countryGDPclass))

# missing cascade variables?
data_missing <- data_cvd %>%
  group_by(Country) %>%
  mutate(n = n()) %>%
  summarize(across(.cols = c(p_id, 
                             psu_num, 
                             stratum_num, 
                             bpms_hypt,
                            bpms_hypt_med,
                            bpms_hypt_med_ctl, 
                            wealth_quintile),
                list(~sum(is.na(.)),
                ~n()))) 
# Armenia missing stratum information (Aug 30)

# set survey weight parameters
# with survey package
data5 <- data_cvd %>%
  as_survey_design(
    stratum = stratum_num, 
    ids = c(psu_num), 
    weights = w_bp,
    variables = c(
      Country,
      clin_hypt,
      bpms_hypt,
      bpms_hypt_med,
      bpms_hypt_med_ctl,
      wealth_quintile
    )
  )

# Overall
# get weighted proportions 
  # out of whole dataset of hypertensives, get proportion that are each variable/step in the cascade

data_n <- data5 %>%
  group_by(Country) %>%
  summarize(n_htns = survey_total(clin_hypt, vartype = "ci"),
            prop_aware = survey_mean(bpms_hypt, proportion = T, vartype = "ci"),
            prop_tx = survey_mean(bpms_hypt_med, proportion = T, vartype = "ci"),
            prop_control = survey_mean(bpms_hypt_med_ctl, proportion = T, vartype = "ci")) %>%
  mutate_at(vars(prop_aware:prop_control_upp), ~(round((. * 100),2)))

# By Quintile
# summarize cascade proportions with weights
data_q <- data5 %>%
  group_by(Country, wealth_quintile) %>%
  summarize(n_htns = survey_total(clin_hypt, vartype = "ci"),
            prop_aware = survey_mean(bpms_hypt, proportion = T, vartype = "ci"),
            prop_tx = survey_mean(bpms_hypt_med, proportion = T, vartype = "ci"),
            prop_control = survey_mean(bpms_hypt_med_ctl, proportion = T, vartype = "ci")) %>%
  mutate_at(vars(prop_aware:prop_control_upp), ~(round((. * 100),2)))

# by quintile linkage rate (from aware to treated,ie slope of line from aware to treated)
data_q <- data_q %>%
  mutate(linkage = prop_tx/prop_aware)

#cascade_q_data2$cascade_variable <- factor(cascade_q_data$cascade_variable, 
#                                          levels = c("prop_aware", "prop_tx", "prop_control"))

saveRDS(data_n, file = "3 Output/overall_cascades.rds")
saveRDS(data_q, file = "3 Output/quintile_cascades.rds")


## r Shape data for ggplot
# load cascades by quintiles graphs

data_q <- readRDS("3 Output/quintile_cascades.rds")

#get data into long format for ggplot
cascade_q_data <- data_q %>%
  select(Country, wealth_quintile, 
         prop_aware, 
         prop_tx,  
        prop_control) %>%
  pivot_longer(prop_aware:prop_control, names_to = "cascade_variable") 

#shape lower bound to merge back in
lower <- data_q %>%
  select(Country, wealth_quintile, 
         prop_aware_low, 
         prop_tx_low,
         prop_control_low) %>%
  pivot_longer(prop_aware_low:prop_control_low, names_to = "cascade_variable") %>%
  mutate(cascade_variable = case_when(cascade_variable == "prop_aware_low"  ~ "prop_aware",
                                      cascade_variable == "prop_tx_low"  ~ "prop_tx",
                                      cascade_variable == "prop_control_low" ~ "prop_control",
                                      TRUE ~ cascade_variable)) %>%
  select(Country, wealth_quintile,cascade_variable,
         lower = value)

#shape upper bound to merge back in
upper <- data_q %>%
  select(Country, wealth_quintile, 
         prop_aware_upp, 
         prop_tx_upp,
         prop_control_upp) %>%
  pivot_longer(prop_aware_upp:prop_control_upp, names_to = "cascade_variable") %>%
  mutate(cascade_variable = case_when(cascade_variable == "prop_aware_upp"  ~ "prop_aware",
                                      cascade_variable == "prop_tx_upp"  ~ "prop_tx",
                                      cascade_variable == "prop_control_upp" ~ "prop_control",
                                      TRUE ~ cascade_variable)) %>%
  select(Country, wealth_quintile,cascade_variable,
         upper = value)

#join so have column with cascade variable names in each row and the upper and lower bound values next to it for ggplot format
cascade_q_data2 <- cascade_q_data %>% left_join(lower) %>% left_join(upper)

#factor cascade levels
cascade_q_data2$cascade_variable <- factor(cascade_q_data$cascade_variable, 
                                          levels = c("prop_aware", "prop_tx", "prop_control"))
cascade_q_data2$wealth_quintile <- as.factor(cascade_q_data$wealth_quintile)

cascade_q_data2 <- cascade_q_data2 %>% 
  left_join(gdp)

#cascade_q_data2$countryGDPclass <- factor(cascade_q_data2$countryGDPclass,
#                            levels = c("1","2", "3"),
#                            labels = c("Low-income", "Lower-middle Income", "Upper-middle Income"))

saveRDS(cascade_q_data2, "3 Output/cascade-graph.rds")

#####Identify best performers#####
#best at each step (irrespective of quintile)
best_step <- cascade_q_data2 %>%
  group_by(cascade_variable) %>%
  filter(value == max(value, na.rm=TRUE))

saveRDS(best_step, file = "3 Output/best_step.rds")

best_step_quintile <-  cascade_q_data2 %>%
  group_by(cascade_variable, wealth_quintile) %>%
  filter(value == max(value, na.rm=TRUE))

saveRDS(best_step_quintile, file = "3 Output/best-step-quintile.rds")

####area under curves####

area <- data_q %>%
  group_by(Country, wealth_quintile) %>%
  summarize(area1 = (prop_aware+prop_tx)/2,
            area2 = (prop_tx+prop_control)/2,
            area_sum = area1 + area2) 

saveRDS(area, file = "3 Output/area-under-quintile-cascades.rds")

best_area <- area %>%
  group_by(wealth_quintile) %>%
  filter(area_sum == max(area_sum, na.rm = T))

saveRDS(best_area, file = "3 Output/best-area-under-quintile-cascades.rds")

```


8. Scenario data file prep
 - keep only hypertensives
 - merge in country-level data: (or keep in separate country/country-quintile dataset?)
    - htn prevalence, auc_gap, countryGDPclass, cascade values
 - set cascade targets by country-quintile and scenario
 - generate baseline cascade performance gap measures/tertiles for graphing stratification
 - join cascade targets and main dataset 
 - select relevant columns
 
 
```{r}

# load Chunk 2 output w/ CVD risk and RR estimates
data_cvd_rr <- readRDS(file = "3 Output/all-w-RRs.rds")
# most recent saved dataset of only htns

#####SETTING CASCADE TARGETS####

# merge in country-level cascade information by quintile in order to estimate additional proportion of individuals who need to be aware and/or treated in each scenario
# will merge this into main dataset

data_q <- readRDS(file = "3 Output/quintile_cascades.rds")

cascades <- data_q %>%
  mutate(prop_aware = as.numeric(prop_aware),
         prop_tx = as.numeric(prop_tx))
rm(data_q)

# figure out target proportion for each country - ie how many of the UNDIAGNOSED hypertensives need to be sample for each country
# load(file = "3 Output/best-step-quintile.rda")
best_step <- readRDS(file = "3 Output/best_step.rds")

# best proportion AWARE
  # 79.85% in Mongolia Q3
aware <- best_step %>%
  filter(cascade_variable == "prop_aware") %>%
  select(value)

#best proportion on TREATMENT
  #70.85% - Q4 in Kazakhstan
tx <- best_step %>%
  filter(cascade_variable == "prop_tx") %>%
  select(value)

#"proportions" are in percents in cascade summary
# input as proportions for sampling
aware_target <- 0.7985

tx_target <- 0.7085

# in percents
# calculate additional people aware and/or on tx in each scenario for each country-quintile
# calculate proportion difference/number of additional people required to be sampled (ie made aware or on tx) in each group (ie country, quintile) to reach targets specified above
cascades2 <- cascades %>%
 # rename(country = Country) %>%
  mutate(across(prop_aware:prop_control_upp, ~./100)) %>% # get into proportions (not percents)
  mutate(addl_aware_prop = aware_target-prop_aware, #additional proportion of htn that need to be identified to reach target (target proportion minus proportion aware)
         addl_aware_und = (addl_aware_prop/(1-prop_aware)), #proportion of the undiagnosed that need to be sampled (ratio)
          addl_tx_prop = tx_target-prop_tx, #additional proportion of htn on tx (target tx prop minus current tx prop)
         addl_tx_untr = (addl_tx_prop/(1-prop_tx))) #additional treatment proportion needed divided by the untreated population to get proportion of untreated need to sample from

#join hypertensives with cascade target country-quintile information
country_cascades <- left_join(data_cvd_rr, cascades2) # join cascade target info (prop_aware, prop_tx needed for scenarios)

# treatment gap
cascades3<- cascades2 %>%
  group_by(Country) %>%
  filter(wealth_quintile == 1 | wealth_quintile == 5) %>%
  pivot_wider(id_cols = c(Country), names_from = wealth_quintile, values_from = prop_tx) %>%
  rename(Q1 = `1`, Q5 = `5`) %>%
  mutate(tx_gap = Q5-Q1) %>%
  ungroup() %>%
  within(tx_gap_rank <- as.integer(cut(tx_gap, quantile(tx_gap, probs=0:3/3), include.lowest=TRUE))) 

saveRDS(cascades3, file = "3 Output/cascades3.rds")

# area under curve gap calculations
area <- readRDS(file = "3 Output/area-under-quintile-cascades.rds")

area2 <- area %>%
  group_by(Country) %>%
  filter(wealth_quintile == 1 | wealth_quintile == 5) %>%
  pivot_wider(id_cols = c(Country), names_from = wealth_quintile, values_from = area_sum) %>%
  rename(Q1 = `1`, Q5 = `5`) %>%
  mutate(auc_gap = Q5-Q1) %>%
  ungroup() %>%
  within(auc_gap_rank <- as.integer(cut(auc_gap, quantile(auc_gap, probs=0:3/3), include.lowest=TRUE))) %>%
  select(Country, auc_gap_rank)

saveRDS(area2, file = "3 Output/area2.rds")

#join hypertensives with cascade target country-quintile information
country_cascades <- left_join(data_cvd_rr, cascades2) %>% # join cascade target info (prop_aware, prop_tx needed for scenarios)
  left_join(cascades3) %>% # join in tx_gap info
  left_join(area2) # join in cascade perf gap info

#dataframe with selected columns for scenario runs
all <- country_cascades %>%
  select(ID,
         Country,
         countryGDPclass, 
         psu_num, 
         rural, 
         stratum_num, 
         w_bp, 
         year, 
         age, 
         educat, 
         sex, 
         wealth_quintile,
         bp_med, 
         clin_hypt,
         sbp,
         und_hypt, 
         bpms_hypt, 
         bpms_hypt_med,
         bpms_hypt_med_ctl,
         bmi,
         csmoke,
         ccodes,
         cvd_reduction,
         cvd_risk:addl_tx_untr,
         tx_gap:auc_gap_rank,
         mean_htn)

saveRDS(all, file = "3 Output/all.rds")

```

8a sensitivity analysis target calculation
 
```{r scenario data prep}

# load Chunk 2 output w/ CVD risk and RR estimates
data_cvd_rr <- readRDS(file = "3 Output/all-w-RRs.rds")
# most recent saved dataset of only htns

#####SETTING CASCADE TARGETS####

# merge in country-level cascade information by quintile in order to estimate additional proportion of individuals who need to be aware and/or treated in each scenario
# will merge this into main dataset

data_q <- readRDS(file = "3 Output/quintile_cascades.rds")

cascades <- data_q %>%
  mutate(prop_aware = as.numeric(prop_aware),
         prop_tx = as.numeric(prop_tx))
rm(data_q)

# ID best performing quintile in each country for sensitivity analysis targets
target <- cascades %>%
  group_by(Country) %>%
  mutate(top_aware = rank(-prop_aware),
         top_tx = rank(-prop_tx)) 
# scenario 1 - aware
target_aware<- target %>%
  filter(top_aware == 1) %>%
  select(Country, 
         prop_aware_target = prop_aware, 
         top_aware) %>%
  distinct()

# scenario 2 - tx
target_tx <- target %>%
  filter(top_tx == 1) %>%
  select(Country, 
         prop_tx_target = prop_tx, 
         top_tx) %>%
  distinct()


# country specific targets for sensitivity analysis
targets <- left_join(target_aware, target_tx) %>%
  select(-top_aware, -top_tx) %>%
  left_join(cascades) %>%
  mutate(prop_aware_target = prop_aware_target/100,
         prop_tx_target = prop_tx_target/100)

# in percents
# calculate additional people aware and/or on tx in each scenario for each country-quintile
# calculate proportion difference/number of additional people required to be sampled (ie made aware or on tx) in each group (ie country, quintile) to reach targets specified above
targets2 <- targets %>%
 # rename(country = Country) %>%
  mutate(across(prop_aware:prop_control_upp, ~./100)) %>% # get into proportions (not percents)
  mutate(addl_aware_prop = prop_aware_target-prop_aware, #additional proportion of htn that need to be identified to reach target (target proportion minus proportion aware)
         addl_aware_und = (addl_aware_prop/(1-prop_aware)), #proportion of the undiagnosed that need to be sampled (ratio)
          addl_tx_prop = prop_tx_target-prop_tx, #additional proportion of htn on tx (target tx prop minus current tx prop)
         addl_tx_untr = (addl_tx_prop/(1-prop_tx))) #additional treatment proportion needed divided by the untreated population to get proportion of untreated need to sample from

#join hypertensives with cascade target country-quintile information
country_cascades_sens <- left_join(data_cvd_rr, targets2) # join cascade target info (prop_aware, prop_tx needed for scenarios)


#dataframe with selected columns for scenario runs
all <- country_cascades_sens %>%
  select(ID,
         Country,
         countryGDPclass, 
         psu_num, 
         rural, 
         stratum_num, 
         w_bp, 
         year, 
         age, 
         educat, 
         sex, 
         wealth_quintile,
         bp_med, 
         clin_hypt,
         sbp,
         und_hypt, 
         bpms_hypt, 
         bpms_hypt_med,
         bpms_hypt_med_ctl,
         bmi,
         csmoke,
         ccodes,
         cvd_reduction,
         cvd_risk:addl_tx_untr,
         mean_htn)

saveRDS(all, file = "3 Output/all-sensitivity.rds")

```

9. Baseline CVD risk calculations

```{r baseline cvd risk}
# start with data_cvd_rr dataset
# full dataset (of hypertensives) with RRs (won't use for baseline calculation though)

#data_cvd <- readRDS(file= "3 Output/analysis-w-cvd.rds")
all <- readRDS("3 Output/all.rds")

# set survey design
baseline <- all %>%
  as_survey_design(
    stratum = stratum_num,
    ids = c(psu_num),
    weights = w_bp)

#weighted mean of CVD risk in baseline
mean_risk_b <- baseline %>%
  group_by(Country, wealth_quintile) %>%
  summarize(mean_cvd_risk_b = survey_mean(cvd_risk, vartype = "ci"))

saveRDS(mean_risk_b, "3 Output/baseline-calcs.rds")

baseline_risk <- readRDS("3 Output/baseline-calcs.rds")
  
```

