---
title: "Pre-scenario coding"
author: "Dorit Stein"
date: "6/21/23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(readxl)
library(astsa)
library(fuzzyjoin)
library(plm)
library(tidyverse)
library(purrr)
library(knitr)
library(haven)
library(srvyr)
library(survey)
library(vroom)
library(data.table)
library(janitor)
library(qdapRegex)

library(globorisk)


```

1. Load cleaned data

```{r data}

data <- read_csv("1 Raw Data/cleaned_final.csv") # August 31, 2022

```

2. Select countries for analytical sample and clean other variables
 - unique PSUs
 - check missingness: Select countries for analysis with <35.5% missingness for wealth_quintile variable
    (other high missing countries were already filtered out in data cleaning)
 - drop missing wealth_quintile individuals (now have complete.case dataset)
 - filter out implausible sbp values
 - fix countryGDPclass

```{r analytical sample}

# Make sure psu_num really is unique within each country
data <- data %>% 
  mutate(psu_num = str_c(Country, psu, sep = "_"),
         stratum_num = stratum)

# drop countries with > 0.355 missingness for wealth_quintile
# pct_na_wealth
data2 <- data %>%
  filter(pct_na_wealth < 0.355)

# countries to include - 52 total
countries <- unique(data2$Country)

# clean year
# drop missing wealth_quintile individuals (complete.cases dataset now)
# filter out implausible sbp
data3 <- data2 %>%
  drop_na(wealth_quintile) %>% 
  mutate(year = ifelse(year == "2015-2016", "2015",
                ifelse(year == "2009-10", "2009",
                ifelse(year == "2009-11", "2010", 
                ifelse(year == "2009-12", "2011",
                ifelse(year == "2014-15", "2014",
                ifelse(year == "2005-6", "2005",
                ifelse(year == "2007/8", "2007", year)))))))) %>%
  rowid_to_column("ID") %>%
  mutate(Country = case_when(Country == "Swaziland" ~ "Eswatini",
                             TRUE ~ Country)) %>%
  filter(sbp <= 270 & sbp >= 70) %>%
  mutate(countryGDPclass = case_when(countryGDPclass == "Low Income Country" ~ "1",
                                     countryGDPclass == "Lower-middle Income Country" ~ "2",
                                     countryGDPclass == "Upper-middle Income Country" ~ "3",
                                     TRUE ~ countryGDPclass))

data3$countryGDPclass <- factor(data3$countryGDPclass,
                            levels = c("1","2", "3"),
                            labels = c("Low-income", "Lower-middle Income", "Upper-middle Income"))
data3$wealth_quintile2 <- factor(data3$wealth_quintile,
                                     levels = c("1", "2", "3", "4", "5"),
                                     labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))

# Aug 29, 2022 (with htn/non-htns, complete.cases for relevant variables)
saveRDS(data3, "3 Output/data.rds") 

```

3. Hypertension prevalence estimates (country, country-quintile level)
 - using analytical sample with complete.cases for relevant variables
 - by country, and by country-quintile
 
```{r htn prevalence}

data3 <- readRDS("3 Output/data.rds")

# set survey design for hypertension prevalence estimates by country, and country-quintile
data_htn <- data3 %>%
  as_survey_design(
    stratum = stratum_num,
    ids = c(psu_num),
    weights = w_bp)

##weighted mean of hypertensives by country and country-quintile

# by country
htn <- data_htn %>%
  group_by(Country) %>%
  summarize(mean_htn = survey_mean(clin_hypt, vartype = "ci"))

# save
saveRDS(htn, file ="3 Output/htn-country.rds")

# by country-quintile
htn_quintile <- data_htn %>%
  group_by(Country, wealth_quintile) %>%
  summarize(
    mean_htn = survey_mean(clin_hypt, vartype = "ci"))

# save
saveRDS(htn_quintile, file ="3 Output/htn-quintile.rds")

# merge in htn prevalence data to main dataset
data4 <- data3 %>%
  left_join(htn)

saveRDS(data4, "3 Output/data4.rds")

```

4. Weights for RRs from GBD (country/sex/age-group)
 - get country/sex/age-group proportions of deaths from IHD vs CHD to weight RRs by, from GBD

```{r GBD rr weights}

# load GBD data
# Accessed Monday January 10th 2022

gbd <- read.csv("1 Raw Data/IHMD-GBD-CVD-Data-Jan.10.2022/IHME-GBD_2019_DATA-8de51a8d-1.csv")

head(gbd)

countries_gbd <- unique(gbd$location_name)

measures <- unique(gbd$measure_name)

causes <- unique(gbd$cause_name)

cause_id <- unique(gbd$cause_id)

# measures - incidence and death
# metrics - number or percent
# cause_name - 
#[1] "Cardiovascular diseases"              "Rheumatic heart disease"              "Ischemic heart disease"              
#[4] "Stroke"                               "Non-rheumatic valvular heart disease" "Cardiomyopathy and myocarditis"      
#[7] "Hypertensive heart disease" 
# cause_id - want 
# stroke - 494
# IHD - 493

# get total sum of IHD and stroke deaths/incidence
# get proportion IHD and stroke represent of total for each country-age-sex grouping
gbd2 <- gbd %>%
  filter(cause_id == 493 | cause_id == 494) %>%
  filter(metric_name == "Number") %>%
  filter(measure_name == "Deaths") %>%
  filter(sex_id != 3) %>%
  mutate(Country = location_name) %>%
  group_by(Country, measure_name, sex_id, sex_name, age_id, age_name) %>%
  mutate(total = sum(val)) %>%
  ungroup() %>%
  mutate(prop = val/total) %>%
  group_by(Country, measure_name, sex_id, sex_name, age_id, age_name) %>%
  mutate(sum_w = sum(prop)) %>%
  ungroup()

# pull out country names
countries <- c(unique(data3$Country))

# filter countries to get ratios of stroke vs IHD
# make uppercase, rename some to match

gbd3 <- gbd2 %>%
  mutate(Country = case_when(Country == "Lao People's Democratic Republic" ~ "Laos",
                             Country == "Iran (Islamic Republic of)" ~ "Iran",
                             Country == "Republic of Moldova" ~ "Moldova",
                             Country == "Saint Vincent and the Grenadines" ~ "St. Vincent & the Grenadines",
                             Country == "United Republic of Tanzania" ~ "Tanzania",
                             Country == "Timor-Leste" ~ "Timor Leste",
                                  TRUE ~ Country),
         sex = case_when(sex_id == 1 ~ 0,
                         sex_id == 2 ~ 1,
                         TRUE ~ NA_real_)) %>%
  filter(Country %in% countries) %>%
  select(sex, age_id, age_name, cause_name, -year, Country, prop) %>%
  pivot_wider(values_from = prop, names_from = cause_name) %>%
  rename(prop_ihd = "Ischemic heart disease",
         prop_stroke = "Stroke")

# see which countries matched in population dataset
matched <- sort(c(unique(gbd3$Country)))

# countries that did not match
missing <- setdiff(countries, matched)
#> missing
#[1] "Gambia" Gambia                      
# "Iran" Iran (Islamic Republic of)                        
# "Laos"    Lao People's Democratic Republic                    
#[4] "Moldova"            Republic of Moldova
#"St. Vincent & the Grenadines" 
#"Swaziland"  "Eswatini"                 
#[7] "Tanzania"   United Republic of Tanzania
#"Timor Leste"   Timor-Leste

# save country-level RRs
saveRDS(gbd3, file = "3 Output/gbd-chd-stroke.rds")

```

5. Calculate individual RRs (individual-level data)
 - using Law et al equations
 - using GBD weights from chunk above

```{r RR calculations}

data4 <- readRDS("3 Output/data4.rds")

# calculate sbp change due to one med at standard dose from Law et al equation
  # create 5 year age groups with same labels as GBD 5-year age groups to merge in CHD and Stroke proportion data
  # assign RR for CHD and Stroke depending on 10 year age group from Law et al paper
  # merge in country proportions
  # generate weighted RR for each person if they were to be put on treatment (and apply to their CVD risk score later)

data_sbp <- data4 %>%
  mutate(sex = as.numeric(sex),
         sbp_change = 9.1+(0.10*(sbp-154)),
         age_id = case_when(age >=40 & age<45 ~ 13,
                              age >=45 & age<50 ~ 14, 
                              age >=50 & age<55 ~ 15, 
                              age>=55 & age<60 ~ 16,
                              age>=60 & age<65 ~ 17,
                              age>=65 & age<70 ~ 18,
                              age>=70 & age<75 ~ 19,
                              age>=75 & age<80 ~ 20,
                              age>=80 & age<85 ~ 30,
                              age>=85 & age <90 ~ 31,
                           TRUE ~ NA_real_),
         rr_chd = case_when(age_id == 13 | age_id == 14 ~ 0.49,
                            age_id == 15 | age_id == 16 ~ 0.5,
                            age_id == 17 | age_id == 18 ~ 0.54,
                            age_id == 19 | age_id == 20 ~ 0.6,
                            age_id == 30 | age_id == 31 ~ 0.67,
                                        TRUE ~ NA_real_),
         rr_stroke = case_when(age_id == 13 | age_id == 14 ~ 0.36,
                               age_id == 15 | age_id == 16 ~ 0.38,
                               age_id == 17 | age_id == 18 ~ 0.43,
                               age_id == 19 | age_id == 20 ~ 0.5,
                               age_id == 30 | age_id == 31 ~ 0.67,
                                        TRUE ~ NA_real_),
         rr_chd_adj = rr_chd^(sbp_change/20),
         rr_stroke_adj = rr_stroke^(sbp_change/20)) 

# load GBD data for proportions of deaths due to CHD and Stroke for each country-sex-age group
# from chunk above
gbd3 <- readRDS(file = "3 Output/gbd-chd-stroke.rds")

data_gbd <- data_sbp %>% 
  left_join(gbd3)

# calculate composite adjusted RR for each person
data_cvd_rr <- data_gbd %>%
  mutate(rr_w = (rr_chd_adj*prop_ihd)+(rr_stroke_adj*prop_stroke),
         cvd_reduction = rr_w)

# save
saveRDS(data_cvd_rr, file = "3 Output/all-w-RRs.rds")

```

6. Globorisk
 - individual CVD risk calculations

```{r globorisk}

data_cvd_rr <- readRDS("3 Output/all-w-RRs.rds")

#run dataset into globorisk to get 10-year CVD risk for each person (line) in the dataset
data_cvd <- data_cvd_rr %>%
  mutate(cvd_risk = globorisk::globorisk(
  sex = sex,
  age = age,
  sbp = sbp,
  smk = csmoke,
  bmi = bmi,
  iso = ccodes,
  year = year, 
  version = "office",
  type = "risk")
) 

#save 
saveRDS(data_cvd, file= "3 Output/analysis-w-cvd.rds")

```

# AMONG HYPERTENSIVES ONLY

7. Cascade performance summary 
 - summarize cascade for each country-quintile
 - select "best performers" at each step (create column in dataset with best performer value?)
 - AUC gap calculations

```{r cascades summary}

data_cvd <- readRDS(file= "3 Output/analysis-w-cvd.rds") %>%
  filter(clin_hypt == 1)

saveRDS(data_cvd, "3 Output/all-w-RRs.rds") # use this in next chunk

gdp <- data_cvd %>%
  group_by(Country) %>%
  summarize(countryGDPclass = unique(countryGDPclass))

# missing cascade variables?
data_missing <- data_cvd %>%
  group_by(Country) %>%
  mutate(n = n()) %>%
  summarize(across(.cols = c(p_id, 
                             psu_num, 
                             stratum_num, 
                             bpms_hypt,
                            bpms_hypt_med,
                            bpms_hypt_med_ctl, 
                            wealth_quintile),
                list(~sum(is.na(.)),
                ~n()))) 
# Armenia missing stratum information (Aug 30)

# set survey weight parameters
# with survey package
data5 <- data_cvd %>%
  as_survey_design(
    stratum = stratum_num, 
    ids = c(psu_num), 
    weights = w_bp,
    variables = c(
      Country,
      clin_hypt,
      bpms_hypt,
      bpms_hypt_med,
      bpms_hypt_med_ctl,
      wealth_quintile
    )
  )

# Overall
# get weighted proportions 
  # out of whole dataset of hypertensives, get proportion that are each variable/step in the cascade

data_n <- data5 %>%
  group_by(Country) %>%
  summarize(n_htns = survey_total(clin_hypt, vartype = "ci"),
            prop_aware = survey_mean(bpms_hypt, proportion = T, vartype = "ci"),
            prop_tx = survey_mean(bpms_hypt_med, proportion = T, vartype = "ci"),
            prop_control = survey_mean(bpms_hypt_med_ctl, proportion = T, vartype = "ci")) %>%
  mutate_at(vars(prop_aware:prop_control_upp), ~(round((. * 100),2)))

# By Quintile
# summarize cascade proportions with weights
data_q <- data5 %>%
  group_by(Country, wealth_quintile) %>%
  summarize(n_htns = survey_total(clin_hypt, vartype = "ci"),
            prop_aware = survey_mean(bpms_hypt, proportion = T, vartype = "ci"),
            prop_tx = survey_mean(bpms_hypt_med, proportion = T, vartype = "ci"),
            prop_control = survey_mean(bpms_hypt_med_ctl, proportion = T, vartype = "ci")) %>%
  mutate_at(vars(prop_aware:prop_control_upp), ~(round((. * 100),2)))

# by quintile linkage rate (from aware to treated,ie slope of line from aware to treated)
data_q <- data_q %>%
  mutate(linkage = prop_tx/prop_aware)

#cascade_q_data2$cascade_variable <- factor(cascade_q_data$cascade_variable, 
#                                          levels = c("prop_aware", "prop_tx", "prop_control"))

saveRDS(data_n, file = "3 Output/overall_cascades.rds")
saveRDS(data_q, file = "3 Output/quintile_cascades.rds")


## r Shape data for ggplot
# load cascades by quintiles graphs

data_q <- readRDS("3 Output/quintile_cascades.rds")

#get data into long format for ggplot
cascade_q_data <- data_q %>%
  select(Country, wealth_quintile, 
         prop_aware, 
         prop_tx,  
        prop_control) %>%
  pivot_longer(prop_aware:prop_control, names_to = "cascade_variable") 

#shape lower bound to merge back in
lower <- data_q %>%
  select(Country, wealth_quintile, 
         prop_aware_low, 
         prop_tx_low,
         prop_control_low) %>%
  pivot_longer(prop_aware_low:prop_control_low, names_to = "cascade_variable") %>%
  mutate(cascade_variable = case_when(cascade_variable == "prop_aware_low"  ~ "prop_aware",
                                      cascade_variable == "prop_tx_low"  ~ "prop_tx",
                                      cascade_variable == "prop_control_low" ~ "prop_control",
                                      TRUE ~ cascade_variable)) %>%
  select(Country, wealth_quintile,cascade_variable,
         lower = value)

#shape upper bound to merge back in
upper <- data_q %>%
  select(Country, wealth_quintile, 
         prop_aware_upp, 
         prop_tx_upp,
         prop_control_upp) %>%
  pivot_longer(prop_aware_upp:prop_control_upp, names_to = "cascade_variable") %>%
  mutate(cascade_variable = case_when(cascade_variable == "prop_aware_upp"  ~ "prop_aware",
                                      cascade_variable == "prop_tx_upp"  ~ "prop_tx",
                                      cascade_variable == "prop_control_upp" ~ "prop_control",
                                      TRUE ~ cascade_variable)) %>%
  select(Country, wealth_quintile,cascade_variable,
         upper = value)

#join so have column with cascade variable names in each row and the upper and lower bound values next to it for ggplot format
cascade_q_data2 <- cascade_q_data %>% left_join(lower) %>% left_join(upper)

#factor cascade levels
cascade_q_data2$cascade_variable <- factor(cascade_q_data$cascade_variable, 
                                          levels = c("prop_aware", "prop_tx", "prop_control"))
cascade_q_data2$wealth_quintile <- as.factor(cascade_q_data$wealth_quintile)

cascade_q_data2 <- cascade_q_data2 %>% 
  left_join(gdp)

#cascade_q_data2$countryGDPclass <- factor(cascade_q_data2$countryGDPclass,
#                            levels = c("1","2", "3"),
#                            labels = c("Low-income", "Lower-middle Income", "Upper-middle Income"))

saveRDS(cascade_q_data2, "3 Output/cascade-graph.rds")

#cascade_q_data2 <-readRDS("3 Output/cascade-graph.rds")
```

 - select "best performers" at each step (create column in dataset with best performer value?)
 -  AUC gap calculations
  - removed countries with NEGATIVE AUC_gaps (8 countries)
  
```{r auc}

####area under curves####
data_q <- readRDS("3 Output/quintile_cascades.rds")

area <- data_q %>%
  group_by(Country, wealth_quintile) %>%
  summarize(area1 = (prop_aware+prop_tx)/2,
            area2 = (prop_tx+prop_control)/2,
            area_sum = area1 + area2) 

saveRDS(area, file = "3 Output/area-under-quintile-cascades.rds")

# area under curve gap calculations
  # remove countries that have negative auc_gap
area <- readRDS(file = "3 Output/area-under-quintile-cascades.rds")

area2 <- area %>%
  group_by(Country) %>%
  filter(wealth_quintile == 1 | wealth_quintile == 5) %>%
  pivot_wider(id_cols = c(Country), names_from = wealth_quintile, values_from = area_sum) %>%
  rename(Q1 = `1`, Q5 = `5`) %>%
  mutate(auc_gap = Q5-Q1) %>%
  ungroup() %>%
  filter(auc_gap > 0) %>%
  mutate(auc_gap_rank = ntile(auc_gap, 3)) %>%
  select(Country, auc_gap_rank, auc_gap)

# 44 countries
saveRDS(area2, file = "3 Output/area2.rds")

# save names of reverse_gap countries to remove below
reverse_gap <- area %>%
  group_by(Country) %>%
  filter(wealth_quintile == 1 | wealth_quintile == 5) %>%
  pivot_wider(id_cols = c(Country), names_from = wealth_quintile, values_from = area_sum) %>%
  rename(Q1 = `1`, Q5 = `5`) %>%
  mutate(auc_gap = Q5-Q1) %>%
  ungroup() %>%
  filter(auc_gap < 0) %>%
  select(Country, auc_gap)

reverse_gap <- unique(reverse_gap$Country)

saveRDS(reverse_gap, "3 Output/reverse-gap.rds")

```

  ## remove countries with negative AUC

```{r cascade best performers}

# 44 countries

#####Identify best performers#####

# ORIGINAL TARGETS (with negative_gap countries removed)
    
# best at each step (irrespective of quintile)
best_step <- cascade_q_data2 %>%
  filter(!(Country %in% reverse_gap)) %>% # filter out reverse_gap countries
  group_by(cascade_variable) %>%
  filter(value == max(value, na.rm=TRUE)) %>%
  filter(cascade_variable != "prop_control")

saveRDS(best_step, file = "3 Output/best_step.rds")

# NEW TARGETS

# best at each step, BY COUNTRY INCOME GROUP
best_step_income <- cascade_q_data2 %>%
  filter(!(Country %in% reverse_gap)) %>% # filter out reverse_gap countries
  group_by(cascade_variable, countryGDPclass) %>%
  filter(value == max(value, na.rm=TRUE)) %>%
  filter(cascade_variable != "prop_control")

saveRDS(best_step_income, file = "3 Output/best_step_income.rds")

# best at each step, BY BASELINE CASCADE PERFORMANCE
  # by terciles of area under cascade for the best performing quintile in each country

# first make terciles of AUC levels based on largest area under cascade quintile for each country
area <- readRDS(file = "3 Output/area-under-quintile-cascades.rds")

area3 <- area %>%
  group_by(Country) %>%
  filter(!(Country %in% reverse_gap)) %>%
  filter(area_sum == max(area_sum, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(area_sum_rank = ntile(area_sum, 3)) %>%
  select(Country, area_sum_rank, area_sum)

saveRDS(area3, file = "3 Output/area-sum-rankings.rds")

# merge in terciles with data to make targetes
# best at each step, BY COUNTRY INCOME GROUP
best_step_perf <- cascade_q_data2 %>%
  filter(!(Country %in% reverse_gap)) %>% # filter out reverse_gap countries
  left_join(area3) %>%
  group_by(cascade_variable, area_sum_rank) %>%
  filter(value == max(value, na.rm=TRUE)) %>%
  filter(cascade_variable != "prop_control")

saveRDS(best_step_perf, file = "3 Output/best_step_perf.rds")

```


8. Scenario data file prep
 - keep only hypertensives
 - merge in country-level data
    - htn prevalence, auc_gap, countryGDPclass, cascade values
 - set cascade targets by country-quintile and scenario
 - generate baseline cascade performance gap measures/tertiles for graphing stratification
 - join cascade targets and main dataset 
 - select relevant columns
 
 
- load data and filter targets by scenario type
```{r load perf data}

reverse_gap <- readRDS("3 Output/reverse-gap.rds")

# load Chunk 2 output w/ CVD risk and RR estimates
data_cvd_rr <- readRDS(file = "3 Output/all-w-RRs.rds")
# most recent saved dataset of only htns

# terciles of baseline performance
area3 <- readRDS(file = "3 Output/area-sum-rankings.rds")
# countryGDPclass
gdp <- data_cvd_rr %>%
  select(Country, countryGDPclass) %>%
  distinct()

covariates <- left_join(area3, gdp)

saveRDS(gdp, "3 Output/gdp.rds")
saveRDS(covariates, "3 Output/gdp-rank.rds")

# merge in country-level cascade information by quintile in order to estimate additional proportion of individuals who need to be aware and/or treated in each scenario
# will merge this into main dataset

data_q <- readRDS(file = "3 Output/quintile_cascades.rds") # cascade variables in percent

cascades <- data_q %>%
  mutate(prop_aware = as.numeric(prop_aware),
         prop_tx = as.numeric(prop_tx)) %>%
  filter(!(Country %in% reverse_gap)) %>%
  left_join(covariates)

saveRDS(cascades, "3 Output/cascades.rds")

# figure out target proportion for each country - ie how many of the UNDIAGNOSED hypertensives need to be sample for each country

## for overall targets
best_step <- readRDS(file = "3 Output/best_step.rds")

## overall
# best proportion AWARE
aware <- best_step %>%
  filter(cascade_variable == "prop_aware") %>%
  select(value)

#best proportion on TREATMENT
tx <- best_step %>%
  filter(cascade_variable == "prop_tx") %>%
  select(value)

#"proportions" are in percents in cascade summary
# input as proportions for sampling
aware_target <- aware$value/100 # proportion
tx_target <- tx$value/100 # proportion

## for income-group targets
best_step_income <- readRDS(file = "3 Output/best_step_income.rds")

## by income-group
# best proportion AWARE
aware_income <- best_step_income %>%
  filter(cascade_variable == "prop_aware") %>%
  mutate(value = value/100) %>%
  select(aware_target_income = value) %>%
  ungroup() %>%
  select(-cascade_variable)


#best proportion on TREATMENT
tx_income <- best_step_income %>%
  filter(cascade_variable == "prop_tx") %>%
  mutate(value = value/100) %>%
  select(tx_target_income = value) %>%
  ungroup() %>%
  select(-cascade_variable)

## for baseline performance targets
best_step_perf <- readRDS(file = "3 Output/best_step_perf.rds")

## by baseline perf
# best proportion AWARE
aware_perf <- best_step_perf %>%
  filter(cascade_variable == "prop_aware") %>%
  mutate(value = value/100) %>%
  select(aware_target_perf = value) %>%
  ungroup() %>%
  select(-cascade_variable)

#best proportion on TREATMENT
tx_perf <- best_step_perf %>%
  filter(cascade_variable == "prop_tx") %>%
  mutate(value = value/100) %>%
  select(tx_target_perf = value) %>%
    ungroup() %>%
  select(-cascade_variable)

## sensitivity analysis targets
# ID best performing quintile in each country for sensitivity analysis targets
target <- cascades %>%
  group_by(Country) %>%
  mutate(top_aware = rank(-prop_aware),
         top_tx = rank(-prop_tx)) 

# scenario 1 - aware
target_aware_sens <- target %>%
  filter(top_aware == 1) %>%
  mutate(aware_target_sens = prop_aware/100) %>%
  select(Country, 
         aware_target_sens) %>%
  distinct()

# scenario 2 - tx
target_tx_sens <- target %>%
  filter(top_tx == 1) %>%
  mutate(tx_target_sens = prop_tx/100) %>%
  select(Country, 
        tx_target_sens) %>%
  distinct()

## DATASET WITH TARGETS
#cascades <- readRDS("3 Output/cascades.rds")
# join targets (in proportion) with cascade dataset
cascades0 <- cascades %>%
  mutate(aware_target = aware_target, 
         tx_target = tx_target) %>%
  left_join(aware_income) %>%
  left_join(tx_income) %>%
  left_join(aware_perf) %>%
  left_join(tx_perf) %>%
  left_join(target_aware_sens) %>%
  left_join(target_tx_sens) %>%
    mutate(prop_aware = prop_aware/100, # proportions
         prop_tx = prop_tx/100, # proportions
         aware_target_rel = prop_aware + (prop_aware*0.5),
         tx_target_rel = prop_tx + (prop_tx*0.5),
         aware_target_rel = ifelse(aware_target_rel > 1, 1, aware_target_rel), # over 100% target put at 100%
         tx_target_rel = ifelse(tx_target_rel > 1, 1, tx_target_rel), # over 100% target put at 100%
         keep_aware = ifelse(aware_target > prop_aware, 1, 0),
         keep_tx = ifelse(tx_target > prop_tx, 1, 0),
         keep_aware_income = ifelse(aware_target_income > prop_aware, 1, 0),
         keep_tx_income = ifelse(tx_target_income > prop_tx, 1, 0),
         keep_aware_perf = ifelse(aware_target_perf > prop_aware, 1, 0),
         keep_tx_perf = ifelse(tx_target_perf > prop_tx, 1, 0),
         keep_aware_sens = ifelse(aware_target_sens == prop_aware, 0, 1),
         keep_tx_sens = ifelse(tx_target_sens == prop_tx, 0, 1))
  
# save cascades and targets
saveRDS(cascades0, "3 Output/cascades0.rds")

#### save target values
saveRDS(aware, "3 Output/aware-target.rds")
saveRDS(tx, "3 Output/tx-target.rds")
saveRDS(aware_income, "3 Output/aware-target-income.rds")
saveRDS(tx_income, "3 Output/tx-target-income.rds")
saveRDS(aware_perf, "3 Output/aware-target-perf.rds")
saveRDS(tx_perf, "3 Output/tx-target-perf.rds")

```

read-in targets
```{r}
aware<- readRDS("3 Output/aware-target.rds")
tx<- readRDS("3 Output/tx-target.rds")
aware_income <- readRDS("3 Output/aware-target-income.rds")
tx__income <- readRDS("3 Output/tx-target-income.rds")
aware_perf<- readRDS("3 Output/aware-target-perf.rds")
tx_income <- readRDS("3 Output/tx-target-perf.rds")
```


-check for which countries the target is BELOW their baseline awareness or tx level (DONE)
```{r}

cascades0 <- readRDS("3 Output/cascades0.rds")

check_targets <- cascades0 %>%
  select(Country, wealth_quintile, prop_aware, prop_tx,
         area_sum_rank, countryGDPclass,
         aware_target, tx_target,
         aware_target_income, tx_target_income,
         aware_target_perf, tx_target_perf,
         aware_target_sens, tx_target_sens) %>%
  mutate(keep_aware = ifelse(aware_target > prop_aware, 1, 0),
         keep_tx = ifelse(tx_target > prop_tx, 1, 0),
         keep_aware_income = ifelse(aware_target_income > prop_aware, 1, 0),
         keep_tx_income = ifelse(tx_target_income > prop_tx, 1, 0),
         keep_aware_perf = ifelse(aware_target_perf > prop_aware, 1, 0),
         keep_tx_perf = ifelse(tx_target_perf > prop_tx, 1, 0),
         keep_aware_sens = ifelse(aware_target_sens == prop_aware, 1, 0),
         keep_tx_sens = ifelse(tx_target_sens == prop_tx, 0, 1))


saveRDS(country_targets, "3 Output/country-target-values-scenarios.rds")

```


- target setting
```{r set targets}
#####SETTING CASCADE TARGETS####

# in percents
# calculate additional people aware and/or on tx in each scenario for each country-quintile
# calculate proportion difference/number of additional people required to be sampled (ie made aware or on tx) in each group (ie country, quintile) to reach targets specified above
cascades2 <- cascades0 %>%
 # rename(country = Country) %>%
  mutate(across(c(prop_aware_upp, prop_aware_low, prop_tx_upp, prop_tx_low, prop_control, prop_control_upp, prop_control_low), ~./100)) %>% # get into proportions (not percents)
  #additional proportion of htn that need to be identified to reach target (target proportion minus proportion aware)
  #proportion of the undiagnosed that need to be sampled (ratio)
  #additional proportion of htn on tx (target tx prop minus current tx prop)
  #additional tx proportion needed divided by the untreated population to get proportion of untreated need to sample from
        #overall
  mutate(addl_aware_prop = aware_target-prop_aware, 
         addl_aware_und = (addl_aware_prop/(1-prop_aware)), 
         addl_tx_prop = tx_target-prop_tx, 
         addl_tx_untr = (addl_tx_prop/(1-prop_tx)),
         # by income group
         addl_aware_prop_income = aware_target_income-prop_aware, 
         addl_aware_und_income = (addl_aware_prop_income/(1-prop_aware)), 
         addl_tx_prop_income = tx_target_income-prop_tx, 
         addl_tx_untr_income = (addl_tx_prop_income/(1-prop_tx)),
         # by baseline performance
         addl_aware_prop_perf = aware_target_perf-prop_aware, 
         addl_aware_und_perf = (addl_aware_prop_perf/(1-prop_aware)), 
         addl_tx_prop_perf = tx_target_perf-prop_tx, 
         addl_tx_untr_perf = (addl_tx_prop_perf/(1-prop_tx)),
         # sensitivity analysis
         addl_aware_prop_sens = aware_target_sens-prop_aware, 
         addl_aware_und_sens = (addl_aware_prop_sens/(1-prop_aware)), 
         addl_tx_prop_sens = tx_target_sens-prop_tx, 
         addl_tx_untr_sens = (addl_tx_prop_sens/(1-prop_tx)),
         # relative increase (50%)
         addl_aware_prop_rel = aware_target_rel-prop_aware,
         addl_aware_und_rel = (addl_aware_prop_rel/(1-prop_aware)), 
         addl_tx_prop_rel = tx_target_rel-prop_tx, 
         addl_tx_untr_rel = (addl_tx_prop_rel/(1-prop_tx))) 

saveRDS(cascades2, "3 Output/sampling-to-target-values.rds")

#join hypertensives with cascade target country-quintile information
#country_cascades <- left_join(data_cvd_rr, cascades2) 
# join cascade target info (prop_aware, prop_tx needed for scenarios)
#area2<- readRDS(file = "3 Output/area2.rds")
#join hypertensives with cascade target country-quintile information
country_cascades <- left_join(data_cvd_rr, cascades2) %>% # join cascade target info (prop_aware, prop_tx needed for scenarios)
  left_join(area2) # join in cascade perf gap info

### SAVE ANALYSIS DATASET ###
#dataframe with selected columns for scenario runs
all <- country_cascades %>%
  select(ID,
         Country,
         countryGDPclass, 
         psu_num, 
         rural, 
         stratum_num, 
         w_bp, 
         year, 
         age, 
         educat, 
         sex, 
         wealth_quintile,
         bp_med, 
         clin_hypt,
         sbp,
         und_hypt, 
         bpms_hypt, 
         bpms_hypt_med,
         bpms_hypt_med_ctl,
         bmi,
         csmoke,
         ccodes,
         cvd_reduction,
         cvd_risk:addl_tx_untr_rel,
         auc_gap_rank,
         auc_gap,
         mean_htn)

saveRDS(all, file = "3 Output/all.rds")

```

9. Baseline CVD risk calculations

```{r baseline cvd risk}
# start with data_cvd_rr dataset
# full dataset (of hypertensives) with RRs (won't use for baseline calculation though)

#data_cvd <- readRDS(file= "3 Output/analysis-w-cvd.rds")
all <- readRDS("3 Output/all.rds")

# set survey design
baseline <- all %>%
  as_survey_design(
    stratum = stratum_num,
    ids = c(psu_num),
    weights = w_bp)

#weighted mean of CVD risk in baseline
mean_risk_b <- baseline %>%
  group_by(Country, wealth_quintile) %>%
  summarize(mean_cvd_risk_b = survey_mean(cvd_risk, vartype = "ci"))

saveRDS(mean_risk_b, "3 Output/baseline-calcs.rds")

baseline_risk <- readRDS("3 Output/baseline-calcs.rds")
  
```

