---
title: "Scenario code - main analysis"
author: "Dorit Stein"
date: "6/21/23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(readxl)
library(purrr)
library(knitr)
library(srvyr)
library(survey)
library(data.table)
library(furrr)

```


###SCENARIOS

# cluster data load
```{r - input data}

all <- readRDS(file = "/n/holyscratch01/verguet_lab/Everyone/all.rds") %>%
  mutate(country = Country)

```

# my computer data load
```{r - input data}

all <- readRDS(file = "3 Output/all.rds") %>%
  mutate(country = Country)

```

# Prep Scenario Data
- for country-quintiles that are the target in each scenario version (keep_x == 0), use baseline values as outcomes because they are not increasing their coverage at all (i.e. Q2, Russia, Scenario 1 overall)
- for scenario 1 across all scenario subtypes, Niger has 0% linkage to tx for Q2, so use baseline values for Q2 for Niger in Scenario 1

```{r}
# Datasets for each scenario subtype: overall, _income, _perf, _sens

###### Scenario 1
# scenario 1 - overall
all_s1 <- all %>%
  filter(keep_aware == 1) %>%
  filter(linkage > 0)

#nest by country-wealth_quintile so can run sampling on each dataframe for each country
all_s1_nest <- all_s1 %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 1 - income group
all_s1_income <- all %>%
  filter(keep_aware_income == 1) %>%
  filter(linkage > 0) %>%
  select(-addl_aware_und) %>%
  rename(addl_aware_und = addl_aware_und_income)

#nest by country-wealth_quintile so can run sampling on each dataframe for each country
all_s1_nest_income <- all_s1_income %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 1 - baseline performance
all_s1_perf <- all %>%
  filter(keep_aware_perf == 1) %>%
  filter(linkage > 0) %>%
  select(-addl_aware_und) %>%
  rename(addl_aware_und = addl_aware_und_perf)

#nest by country-wealth_quintile so can run sampling on each dataframe for each country
all_s1_nest_perf<- all_s1_perf %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 1 - sensitivity
all_s1_sens <- all %>%
  filter(keep_aware_sens == 1) %>%
  filter(linkage > 0) %>%
  select(-addl_aware_und) %>%
  rename(addl_aware_und = addl_aware_und_sens)

#nest by country-wealth_quintile so can run sampling on each dataframe for each country
all_s1_nest_sens <- all_s1_sens %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 1 - relative increase
all_s1_rel <- all %>%
  filter(linkage > 0) %>%
  select(-addl_aware_und) %>%
  rename(addl_aware_und = addl_aware_und_rel)

#nest by country-wealth_quintile so can run sampling on each dataframe for each country
all_s1_nest_rel <- all_s1_rel %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# remove unnested datasets
rm(all_s1, all_s1_income, all_s1_perf, all_s1_sens, all_s1_rel)

###### Scenario 2
# scenario 2 - overall
all_s2 <- all %>%
  filter(keep_tx == 1) 

#nest into country-quintile dataframes
all_s2_nest <- all_s2 %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 2 - income
all_s2_income <- all %>%
  filter(keep_tx_income == 1) %>%
  select(-addl_tx_untr) %>%
  rename(addl_tx_untr = addl_tx_untr_income) 

#nest into country-quintile dataframes
all_s2_nest_income <- all_s2_income %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 2 - baseline performance
all_s2_perf <- all %>%
  filter(keep_tx_perf == 1) %>%
  select(-addl_tx_untr) %>%
  rename(addl_tx_untr = addl_tx_untr_perf) 

#nest into country-quintile dataframes
all_s2_nest_perf <- all_s2_perf %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 2 - sensitivity analysis
all_s2_sens <- all %>%
  filter(keep_tx_sens == 1) %>%
  select(-addl_tx_untr) %>%
  rename(addl_tx_untr = addl_tx_untr_sens) 

#nest into country-quintile dataframes
all_s2_nest_sens <- all_s2_sens %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# scenario 2 - relative increase
all_s2_rel <- all %>%
  select(-addl_tx_untr) %>%
  rename(addl_tx_untr = addl_tx_untr_rel) 

#nest into country-quintile dataframes
all_s2_nest_rel <- all_s2_rel %>%
  group_by(country, wealth_quintile) %>%
  nest() %>%
  ungroup()

# remove unnested datasets
rm(all_s2, all_s2_income, all_s2_perf, all_s2_sens, all_s2_rel)

```


# Scenario 1 + 2
 - do all the sampling/treating/summarizing for one country-quintile (within one function)
 - then map that function on the nested dataframe

Scenario Functions

```{r - new scenario coding - scenario1}

# alg is dataframe for 1 country-quintile

scenario1 <- function(alg) { # input dataset should include aware/unaware, filter in the fxn below
  
  #set.seed(1234)
  
  prop_sample <- alg$addl_aware_und[1]
  link_rx <- alg$linkage[1]
  
  # filter those unaware of hypertensive status
  # sample from unaware to be put on treatment
  alg1 <- alg %>%
    filter(bpms_hypt != 1) %>% # filter unaware
    slice_sample(prop = prop_sample) |>
    slice_sample(prop = link_rx) |>
    mutate(on_aware_tx = 1) %>%
    select(ID, on_aware_tx)
  
  alg_RR <- alg %>% 
    mutate(on_aware_tx = if_else(ID %in% alg1$ID, 1, 0)) |>
    mutate(cvd_risk_s1 = ifelse(on_aware_tx == 1, cvd_risk*cvd_reduction, cvd_risk), 
           # assign new CVD risk for those on tx
           risk_d_s1 = cvd_risk-cvd_risk_s1,
           # NEW for relative change estimate
           rel_change_s1 = abs((cvd_risk_s1-cvd_risk)/cvd_risk)) 
           # for each individual, take difference from scenario 1 risk and baseline risk
   
   #set survey weights
   scenario1_alg <- alg_RR %>% 
     as_survey_design(
       stratum = stratum_num,
       ids = c(psu_num),
       weights = w_bp)
   
   #weighted mean of CVD risk in scenario 1
   mean_risk_s1 <- scenario1_alg %>%
     summarize(mean_cvd_risk_s1 = survey_mean(cvd_risk_s1),
               mean_risk_d_s1 = survey_mean(risk_d_s1),
               mean_rel_change_s1 = survey_mean(rel_change_s1))
   
   s1_rnorm <- with(mean_risk_s1,
        tibble(mean_cvd_risk_s1_rnorm = rnorm(1000,mean_cvd_risk_s1, mean_cvd_risk_s1_se),
               mean_risk_d_s1_rnorm = rnorm(1000, mean_risk_d_s1, mean_risk_d_s1_se),
               mean_rel_change_s1_rnorm = rnorm(1000, mean_rel_change_s1, mean_rel_change_s1_se)))

  s1_rnorm
     
}

####S1####
# replicate scenario 1 function

replicate_s1 <- function(alg) {
  
  df <- replicate(n = 1000, scenario1(alg), simplify = F)
  
  df2 <- map_dfr(df, as.list) |>
    # pull out mean and 95th UI 
    pivot_longer(cols = mean_cvd_risk_s1_rnorm:mean_rel_change_s1_rnorm) |>
    group_by(name) |> 
    arrange(value) |> 
    mutate(rank = rank(value, ties.method = 'first'),
           mean = as.numeric(mean(value)),
           interval = ifelse(rank == 25000, "lower", "upper")) |> 
    filter(rank == 25000 | rank == 975000) |>
    ungroup() |>
    select(-rank) |>
    pivot_wider(names_from = interval, values_from = value)
    
    df2
  
}

####### Scenario 2 coding

scenario2 <- function(alg) {
  
  #set.seed(1234)
  
  prop_sample <- alg$addl_tx_untr[1]
  
  # sample from untreated to be put on treatment
  alg2 <- alg %>%
    filter(bpms_hypt_med != 1) %>% # filter untreated only
    slice_sample(prop = prop_sample) |>
                 #, weight_by = w_bp) %>%
    mutate(slice_tx = 1) %>%
    select(ID, slice_tx)
  
  alg_RR_2 <- alg %>% 
    mutate(slice_tx = if_else(ID %in% alg2$ID, 1, 0)) |>
    mutate(cvd_risk_s2 = ifelse(slice_tx == 1, cvd_risk*cvd_reduction, cvd_risk),
           # assign new CVD risk for those on tx
           risk_d_s2 = cvd_risk-cvd_risk_s2,
           # NEW for relative change estimate
           rel_change_s2 = abs((cvd_risk_s2-cvd_risk)/cvd_risk)) 
            # for each individual, take difference from scenario 2 risk and baseline risk
   
  #set survey weights
   scenario2_alg <- alg_RR_2 %>%
     as_survey_design(
       stratum = stratum_num,
       ids = c(psu_num),
       weights = w_bp)
  
  #weighted mean of CVD risk in scenario 2
   mean_risk_s2 <- scenario2_alg %>%
     summarize(
       mean_cvd_risk_s2 = survey_mean(cvd_risk_s2),
       mean_risk_d_s2 = survey_mean(risk_d_s2),
       mean_rel_change_s2 = survey_mean(rel_change_s2))
  
     s2_rnorm <- with(mean_risk_s2,
        tibble(mean_cvd_risk_s2_rnorm = rnorm(1000,mean_cvd_risk_s2, mean_cvd_risk_s2_se),
               mean_risk_d_s2_rnorm = rnorm(1000, mean_risk_d_s2, mean_risk_d_s2_se),
               mean_rel_change_s2_rnorm = rnorm(1000, mean_rel_change_s2, mean_rel_change_s2_se)))

  s2_rnorm
  
}

####S2####
# replicate scenario 2 function

replicate_s2 <- function(alg) {
  
  df <- replicate(n = 1000, scenario2(alg), simplify = F)
  
  df2 <- # flatten list into tibbles
    map_dfr(df, as.list) |>
    # pull out mean and 95th UI 
    pivot_longer(cols = mean_cvd_risk_s2_rnorm:mean_rel_change_s2_rnorm) |>
    group_by(name) |> 
    arrange(value) |> 
    mutate(rank = rank(value, ties.method = 'first'),
           mean = as.numeric(mean(value)),
    interval = ifelse(rank == 25000, "lower", "upper")) |> 
            filter(rank == 25000 | rank == 975000) |>
    ungroup() |>
    select(-rank) |>
    pivot_wider(names_from = interval, values_from = value)

  df2
  
}

```

# Run Scenarios

```{r}
# map scenarios onto the nested dataframe for each country-quintile

# OVERALL - s1
plan(multisession)
system.time({
  
s1 <- all_s1_nest |>
  mutate(s1_output = future_map(data, 
                         ~replicate_s1(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
  select(-data)
})

saveRDS(s1, "/n/holyscratch01/verguet_lab/Everyone/s1-overall.rds")

rm(s1)

# OVERALL - s2
# map scenarios onto the nested dataframe for each country-quintile
plan(multisession) 
system.time({
  
s2 <- all_s2_nest |>
  mutate(s2_output = future_map(data, 
                         ~replicate_s2(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
        select(-data)
})

# save clean version
saveRDS(s2, "/n/holyscratch01/verguet_lab/Everyone/s2-overall.rds")

rm(s2)

# INCOME GROUP - s1
plan(multisession)
system.time({
  
s1 <- all_s1_nest_income |>
  mutate(s1_output = future_map(data, 
                         ~replicate_s1(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
  select(-data)
})

saveRDS(s1, "/n/holyscratch01/verguet_lab/Everyone/s1-income.rds")

rm(s1)

# INCOME GROUP - s2
# map scenarios onto the nested dataframe for each country-quintile
plan(multisession) 
system.time({
  
s2 <- all_s2_nest_income |>
  mutate(s2_output = future_map(data, 
                         ~replicate_s2(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
        select(-data)
})

# save clean version
saveRDS(s2, "/n/holyscratch01/verguet_lab/Everyone/s2-income.rds")

rm(s2)

# PERFORMANCE - s1
plan(multisession)
system.time({
  
s1 <- all_s1_nest_perf |>
  mutate(s1_output = future_map(data, 
                         ~replicate_s1(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
  select(-data)
})

saveRDS(s1, "/n/holyscratch01/verguet_lab/Everyone/s1-perf.rds")

rm(s1)

# PERFORMANCE - s2
# map scenarios onto the nested dataframe for each country-quintile
plan(multisession) 
system.time({
  
s2 <- all_s2_nest_perf |>
  mutate(s2_output = future_map(data, 
                         ~replicate_s2(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
        select(-data)
})

# save clean version
saveRDS(s2, "/n/holyscratch01/verguet_lab/Everyone/s2-perf.rds")

rm(s2)

# SENSITIVITY - s1
plan(multisession)
system.time({
  
s1 <- all_s1_nest_sens |>
  mutate(s1_output = future_map(data, 
                         ~replicate_s1(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
  select(-data)
})

saveRDS(s1, "/n/holyscratch01/verguet_lab/Everyone/s1-sens.rds")

rm(s1)

# SENSITIVITY - s2
# map scenarios onto the nested dataframe for each country-quintile
plan(multisession) 
system.time({
  
s2 <- all_s2_nest_sens |>
  mutate(s2_output = future_map(data, 
                         ~replicate_s2(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
        select(-data)
})

# save clean version
saveRDS(s2, "/n/holyscratch01/verguet_lab/Everyone/s2-sens.rds")

rm(s2)

# RELATIVE - s1
plan(multisession)
system.time({
  
s1 <- all_s1_nest_rel |>
  mutate(s1_output = future_map(data, 
                         ~replicate_s1(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
  select(-data)
})

saveRDS(s1, "/n/holyscratch01/verguet_lab/Everyone/s1-rel.rds")

rm(s1)

# RELATIVE - s2
# map scenarios onto the nested dataframe for each country-quintile
plan(multisession) 
system.time({
  
s2 <- all_s2_nest_rel |>
  mutate(s2_output = future_map(data, 
                         ~replicate_s2(.),
                         .options = furrr_options(seed=123L),
                         .progress = TRUE)) |>
        select(-data)
})

# save clean version
saveRDS(s2, "/n/holyscratch01/verguet_lab/Everyone/s2-rel.rds")

rm(s2)

```

