---
title: "CVD Prelim Results Tables and Figures"
author: "Dorit Stein"
date: "1/17/2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, message = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

rm(list = ls())

library(tidyverse)
library(ggrepel)
library(astsa)
library(fuzzyjoin)
library(purrr)
library(knitr)
library(srvyr)
library(scales)
library(survey)
library(globorisk)
library(data.table)
library(countrycode) # turn country codes into pretty names
library(gridExtra)   # a helper for arranging individual ggplot objects
library(ggthemes)    # has a clean theme for ggplot2
library(viridis)     # best. color. palette. evar.
library(knitr)       # kable : prettier data.frame output
## tableone package itself
library(tableone)
library(kableExtra)
library(iNZightTools) # for survey_IQR

library(paletteer)
library(ggforce)

library(tidyverse)
library(hrbrthemes)
library(patchwork)
library(GGally)
library(viridis)

```

# LOAD DATA + make adjustments

# Add baseline values in for senario outcomes for targets + Niger
Scenario 1:
-mean cvd risk is same as baseline for Niger Q2, Mongolia Q3
  -mean difference in cvd cases: 0
  -mean % change in cvd cases: 0
  -mean cvd risk: baseline value
Scenario 2:
-mean cvd risk is same as baseline for Kazakhstan Q4
  -mean differnece in cvd cases: 0
  -mean % change in cvd cases: 0
  -mean cvd risk: baseline value

```{r load data}
# scenario results separately
s1_calcs <- readRDS("3 Output/s1_calcs.rds")
s2_calcs <- readRDS("3 Output/s2_calcs.rds")
baseline2 <- readRDS("3 Output/baseline2.rds")

# combined results
scenario_calcs <- readRDS("3 Output/all-scenarios.rds") 
scenario_calcs_baseline <- readRDS("3 Output/all-scenarios-baseline.rds") 

#relative combined results
scenario_calcs_rel <- scenario_calcs %>%
  filter(measure == "mean_rel_c")
# absolute combined results
scenario_calcs_abs <- scenario_calcs %>%
  filter(measure == "mean_risk_d")

# full dataset
all <- readRDS(file = "3 Output/all.rds") %>%
  mutate(country = Country)

# ccodes
ccodes <- all %>%
  select(country, ccodes) %>%
  distinct()

# countrygdp class
gdp <- all %>%
  select(country, countryGDPclass) %>%
  distinct()

# merge in relevant country-quintile level info?

# create graphing datasets
# add in baseline values for missing target country-quintiles+Niger
  #Mongolia Q3 - Scenario 1
  #Niger Q2 - Scenario 1
  #Kazakhstan - Q4 - Scenario 2
## fixing targets + Niger in scenario outcomes)
mong <- baseline2 |>
  filter(country == "Mongolia" & wealth_quintile == "3") |>
  mutate(scenario = case_when(scenario == "Baseline" ~ "Scenario 1: Diagnosis"))

niger <- baseline2 |>
  filter(country == "Niger" & wealth_quintile == "2") |>
  mutate(scenario = case_when(scenario == "Baseline" ~ "Scenario 1: Diagnosis"))

kaz <- baseline2 |>
  filter(country == "Kazakhstan" & wealth_quintile == "4") |>
    mutate(scenario = case_when(scenario == "Baseline" ~ "Scenario 2: Treatment"))
## end fixing

mean_risk <- scenario_calcs_baseline |>
  filter(name == "Mean CVD Risk (%)") |>
  rbind(mong, kaz, niger) |> # add in Mong, Kaz, Niger baseline values as scenario outcomes
  left_join(ccodes)

# for figure 1

mean_risk$wealth_quintile <- factor(mean_risk$wealth_quintile,
                                     levels = c("1", "2", "3", "4", "5"),
                                      labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))

difference <- mean_risk %>% 
  arrange(country, scenario, wealth_quintile) %>%
  mutate(mean = ifelse(is.na(lower), mean, paste0(mean))) %>%
  dplyr::select(country,
                scenario, 
         wealth_quintile, 
         mean)  %>%
  pivot_wider(names_from = "wealth_quintile", values_from = "mean") %>%
  mutate(difference5_1 = as.numeric(Q5)-as.numeric(Q1),
         difference1_5 = as.numeric(Q1)-as.numeric(Q5),
         difference_abs = abs(difference1_5))


gap <- readRDS("3 Output/area2.rds") %>% rename(country = Country)

## to add 0 mean diff and 0 rel change for targets + Niger in scenario 1/2
niger_a <- scenario_calcs_abs |>
  filter(country == "Niger" & wealth_quintile == "2") |>
  mutate(scenario = case_when(scenario == "Scenario 2: Treatment" ~ "Scenario 1: Diagnosis"),
         mean = 0,
         lower = 0,
         upper = 0)

mong_a <- scenario_calcs_abs |>
  filter(country == "Mongolia" & wealth_quintile == "3") |>
  mutate(scenario = case_when(scenario == "Scenario 2: Treatment" ~ "Scenario 1: Diagnosis"),
         mean = 0,
         lower = 0,
         upper = 0)

kaz_a <- scenario_calcs_abs |>
  filter(country == "Kazakhstan" & wealth_quintile == "4") |>
  mutate(scenario = case_when(scenario == "Scenario 1: Diagnosis" ~ "Scenario 2: Treatment"),
         mean = 0,
         lower = 0,
         upper = 0)

niger_r <- scenario_calcs_rel |>
  filter(country == "Niger" & wealth_quintile == "2") |>
  mutate(scenario = case_when(scenario == "Scenario 2: Treatment" ~ "Scenario 1: Diagnosis"),
         mean = 0,
         lower = 0,
         upper = 0)

mong_r <- scenario_calcs_rel |>
  filter(country == "Mongolia" & wealth_quintile == "3") |>
  mutate(scenario = case_when(scenario == "Scenario 2: Treatment" ~ "Scenario 1: Diagnosis"),
         mean = 0,
         lower = 0,
         upper = 0)

kaz_r <- scenario_calcs_rel |>
  filter(country == "Kazakhstan" & wealth_quintile == "4") |>
  mutate(scenario = case_when(scenario == "Scenario 1: Diagnosis" ~ "Scenario 2: Treatment"),
         mean = 0,
         lower = 0,
         upper = 0)
##

abs <- scenario_calcs_abs %>%
  rbind(kaz_a, mong_a, niger_a) %>%
  left_join(gdp) %>%
  left_join(gap) %>%
    mutate(scenario = case_when(scenario == "Baseline" ~ "Baseline",
                                scenario == "Scenario 1: Diagnosis" ~ "Diagnosis scenario",
                                scenario == "Scenario 2: Treatment" ~ "Treatment scenario"))

rel <- scenario_calcs_rel %>%
  rbind(kaz_r, mong_r, niger_r) %>%
  left_join(gdp) %>%
  left_join(gap)
  
# to add later
#   mutate(countryGDPclass = case_when(countryGDPclass == "Low Income Country" ~ "1",
#                                      countryGDPclass == "Lower-middle Income Country" ~ "2",
#                                      countryGDPclass == "Upper-middle Income Country" ~ "3",
#                                      TRUE ~ countryGDPclass))
# 
abs$auc_gap_rank <- factor(abs$auc_gap_rank,
                            levels = c("1","2", "3"),
                            labels = c("Low Gap", "Mid Gap", "High Gap"))
abs$wealth_quintile <- factor(abs$wealth_quintile,
                                     levels = c("1", "2", "3", "4", "5"),
                                      labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))
rel$auc_gap_rank <- factor(rel$auc_gap_rank,
                            levels = c("1","2", "3"),
                            labels = c("Low Gap", "Mid Gap", "High Gap"))
rel$wealth_quintile <- factor(rel$wealth_quintile,
                                     levels = c("1", "2", "3", "4", "5"),
                                      labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))

#mean_risk$wealth_quintile <- factor(mean_risk$wealth_quintile,
#                                     levels = c("1", "2", "3", "4", "5"),
#                                      labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))

cascades <- readRDS("3 Output/cascade-graph.rds")

# to load into appendix file later
saveRDS(abs, "3 Output/abs.rds")
saveRDS(rel, "3 Output/rel.rds")
saveRDS(mean_risk, "3 Output/mean_risk.rds")

saveRDS(difference, "3 Output/difference-cvd-risk.rds")

#colors for quintile groups
blu_purp <- c("#8c96c6","#8c6bb1", "#88419d", "#810f7c", "#4d004b")
green <- c("#78c679", "#41ab5d", "#238443", "#005a32", "#004529")
purp_pink <- c("#f768a1", "#dd3497", "#ae017e", "#7a0177", "#49006a")
purple <- c("#9e9ac8", "#807dba", "#6a51a3", "#54278f", "#3f007d")
green_blu <- c("#67a9cf", "#3690c0", "#02818a", "#016c59", "#014636")
red<- c("#fc8d59", "#ef6548", "#d7301f", "#b30000", "#7f0000")
red_yellow<- c("#fe9929", "#ec7014", "#cc4c02", "#993404", "#662506")
blues<- c("#6baed6", "#4292c6", "#2171b5", "#08519c", "#08306b")
```

# load scenario results
Calculate # of cases by quintile etc 

```{r}
# from 3 results tables script
abs2 <- readRDS("3 Output/abs.rds")
#saveRDS(rel, "3 Output/rel.rds")

htn_quintile <- readRDS(file ="3 Output/htn-quintile.rds")
pop_quintile <- readRDS(file = "3 Output/pop_quint_forty_plus.rds") # from "A Population Totals.RMD" script

data <- left_join(htn_quintile, pop_quintile)

htn_n <- data %>%
  mutate(number_htn = round(mean_htn*quintile_pop,0)) %>%
  rename(country = Country)  

htn_n$wealth_quintile <- factor(htn_n$wealth_quintile,
                                     levels = c("1", "2", "3", "4", "5"),
                                      labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))

htn_abs <- htn_n %>%
  left_join(abs2) %>%
  mutate(per_diff = mean/1000,
         abs_case_diff = number_htn*per_diff) %>%
    mutate(scenario = case_when(scenario == "Baseline" ~ "Baseline",
                                scenario == "Scenario 1: Diagnosis" ~ "Diagnosis scenario",
                                scenario == "Scenario 2: Treatment" ~ "Treatment scenario"))  

# no weights (i.e. weighted by population/number of htns - bigger countries contribute more to the numbers)
abs_diff <- htn_abs %>%
  group_by(wealth_quintile, scenario) %>%
  summarize(abs_case_diff = sum(abs_case_diff, na.rm = T)) %>%
  ungroup() %>%
  group_by(scenario) %>%
  mutate(sum = sum(abs_case_diff),
         prop = abs_case_diff/sum)

# proportion of cases in bottom quintiles BY COUNTRY - take average (like equal weighting?)
abs_diff <- htn_abs %>%
  group_by(country, wealth_quintile, scenario) %>%
  mutate(abs_case_diff = sum(abs_case_diff, na.rm = T),
            n_htn = sum(number_htn)) %>%
  ungroup() %>%
  group_by(country, scenario) %>%
  mutate(sum = sum(abs_case_diff),
         prop = abs_case_diff/sum,
         sum_htn = sum(n_htn),
         prop_htn = n_htn/sum_htn) 

# avg by scenario
abs_diff_avg_overall <- abs_diff %>%
  group_by(wealth_quintile, scenario) %>%
 summarize(avg_diff = mean(prop),
            avg_htn_prop = mean(prop_htn)) 

write.csv(abs_diff_avg_overall, "3 Output/avg-prop-cases-averted.csv")

# long
abs_diff_avg <- abs_diff %>%
  group_by(wealth_quintile, scenario) %>%
 summarize(avg_diff = mean(prop),
            avg_htn_prop = mean(prop_htn)) %>%
  pivot_longer(cols = avg_diff:avg_htn_prop)

# avg by GDP
abs_diff_avg <- abs_diff %>%
  group_by(wealth_quintile, scenario, countryGDPclass) %>%
 summarize(avg_diff = mean(prop),
            avg_htn_prop = mean(prop_htn)) %>%
  pivot_longer(cols = avg_diff:avg_htn_prop)

# total abs cases averted
abs_diff_total <- htn_abs %>%
  group_by(scenario) %>%
  mutate(sum_scenario = sum(abs_case_diff))

abs_diff_total2<- abs_diff_total %>%
  group_by(scenario, wealth_quintile) %>% 
  summarize(abs_case_diff = round(sum(abs_case_diff, na.rm = T),0),
            prop_cases = round((abs_case_diff/sum_scenario), 3)) %>%
  unique()

write.csv(abs_diff_total2, "3 Output/total-cases-averted.csv")

abs_diff_total_lmic <- htn_abs %>%
  group_by(scenario, countryGDPclass) %>%
  mutate(sum_scenario = sum(abs_case_diff))

abs_diff_total3<- abs_diff_total_lmic %>%
  group_by(scenario, wealth_quintile, countryGDPclass) %>% 
  summarize(abs_case_diff = round(sum(abs_case_diff, na.rm = T),0),
            prop_cases = round((abs_case_diff/sum_scenario), 3)) %>%
  unique()

abs_diff_total4 <- abs_diff_total_lmic %>%
  group_by(scenario, wealth_quintile, countryGDPclass) %>% 
  summarize(abs_case_diff = round(sum(abs_case_diff, na.rm = T),0),
            total_htns = sum(number_htn),
            per_capita_averted = abs_case_diff/total_htns,
            averted_rate = round((per_capita_averted*1000),2)) %>%
  unique()

```


# Table 1 

```{r}

data_table1 <- all %>%
  as_survey_design(
    stratum = stratum_num,
    ids = c(psu_num),
    weights = w_bp,
    variables = c(country, age, sex, bmi, csmoke, sbp))

country_n <- data_table1 %>%
  group_by(country) %>%
  summarize(Number=n())

saveRDS(country_n, "3 Output/country_n.rds")

#country_n <- readRDS("3 Output/country_n.rds")

table1_median <- data_table1 %>%
  group_by(country) %>%
  summarize(Age = survey_median(age),
            age_high = max(age),
            age_low = min(age),
         Female = survey_mean(sex),
         BMI = survey_median(bmi),
         bmi_iqr = survey_quantile(bmi, quantiles = c(0.25, 0.75)),
         Smoking = survey_mean(csmoke),
         SBP = survey_median(sbp),
         sbp_iqr =survey_quantile(sbp, quantiles = c(0.25, 0.75)))

# htn prev
htn <- readRDS("3 Output/htn-country.rds")
htn2 <- htn %>%
    mutate(across(c(mean_htn, mean_htn_low, mean_htn_upp), ~format(round(.*100, digits=1)))) %>%
  rename(country = Country)

# merge htn prev, country N          
table1_2 <- table1_median %>% 
  left_join(htn2) %>% 
  left_join(country_n) 
#%>%
  #mutate(across(c(mean_htn, mean_htn_low, mean_htn_upp), ~format(round(.*100, digits=1))))

saveRDS(table1_2, "3 Output/table1-unformatted.rds")

table1_2 <- readRDS("3 Output/table1-unformatted.rds")

#table1_median <- readRDS("3 Output/table1-unformatted.rds")

countries <- table1 %>%
  select(country)

# Formatted table 1 dataframe
table1_format <- table1_2 %>%
  select(-c(Age_se, Female_se, BMI_se, bmi_iqr_q25_se, bmi_iqr_q75_se, Smoking_se, SBP_se, sbp_iqr_q25_se,
            sbp_iqr_q75_se)) %>%
  mutate(across(!country, ~as.numeric(.))) %>%
  #mutate(n = format(round(as.numeric(n), digits=0), nsmall = 0),
  #       Age = format(round(Age, digits=0), nsmall = 0),
  #       age_high = format(round(age_high, digits=0), nsmall = 0),
  #       age_low = format(round(age_low, digits=0), nsmall = 0)) %>%
  mutate(across(c(Female, Smoking), ~.*100)) %>%
  mutate(across(c(Age, Female, age_high, age_low), ~format(round(., digits=0), nsmall = 0))) %>%
  mutate(across(!c(country, Age, Female, age_high, age_low), ~format(round(., digits=1), nsmall = 1))) %>%
  #mutate(across(c(n, Age, age_high, age_low), ~format(round(., digits=0), nsmall = 1))) %>%
  transmute(Country = country,
            "N*" = round(as.numeric(Number),0),
            "Median Age" = Age,
            "Age Range" = paste0(age_low, "-", age_high),
            "Female (%)" = paste0(Female),
            "Median BMI (IQR)" = paste0(BMI, " ","(", bmi_iqr_q25, ",", bmi_iqr_q75, ")"),
            "Currently Smoking (%)" = paste0(Smoking),
            "Median SBP (IQR)" = paste0(SBP, " ","(", sbp_iqr_q25, ",", sbp_iqr_q75, ")"),
            "Hypertension Prevalence (95% CI)" = paste0(mean_htn, " ","(", mean_htn_low, ",", mean_htn_upp, ")"))

# Formatted table output
#kable(table1_format) %>% kable_styling(latex_options = c("HOLD_position", "scale_down"))

kbl(table1_format, caption = "Table 1: Weighted distribution of cardiovascular disease risk factors in participants ages 40-80 years from population-based surveys conducted in 52 low- and middle-income countries", booktabs = T) %>% kable_styling(latex_options = c("striped", "hold_position")) %>%
  footnote(symbol = c("Unweighted sample size", "Among total population in each country"), footnote_as_chunk = T)

saveRDS(table1_format, "3 Output/table1-formatted.rds")

#outputted to Word in script: '4 Table 1 to Word'

```

# Figure 1
Calculate mean + 95% CI for country groups (low, low-middle, middle-income)

```{r calculate cascades by country level income group}

# set survey weight parameters
# with survey package
data5 <- all %>%
  as_survey_design(
    stratum = stratum_num, 
    ids = c(psu_num), 
    weights = w_bp,
    variables = c(
      Country,
      clin_hypt,
      bpms_hypt,
      bpms_hypt_med,
      bpms_hypt_med_ctl,
      wealth_quintile,
      countryGDPclass
    )
  )

# Overall
# get weighted proportions 
  # out of whole dataset of hypertensives, get proportion that are each variable/step in the cascade

data_n <- data5 %>%
  group_by(countryGDPclass, wealth_quintile) %>%
  summarize(prop_aware = survey_mean(bpms_hypt, proportion = T, vartype = "ci"),
            prop_tx = survey_mean(bpms_hypt_med, proportion = T, vartype = "ci"),
            prop_control = survey_mean(bpms_hypt_med_ctl, proportion = T, vartype = "ci")) %>%
  mutate_at(vars(prop_aware:prop_control_upp), ~(round((. * 100),2)))

#get data into long format for ggplot
cascade_q_data <- data_n %>%
  select(countryGDPclass, wealth_quintile, 
         prop_aware, 
         prop_tx,  
        prop_control) %>%
  pivot_longer(prop_aware:prop_control, names_to = "cascade_variable") 

#shape lower bound to merge back in
lower <- data_n %>%
  select(countryGDPclass, wealth_quintile, 
         prop_aware_low, 
         prop_tx_low,
         prop_control_low) %>%
  pivot_longer(prop_aware_low:prop_control_low, names_to = "cascade_variable") %>%
  mutate(cascade_variable = case_when(cascade_variable == "prop_aware_low"  ~ "prop_aware",
                                      cascade_variable == "prop_tx_low"  ~ "prop_tx",
                                      cascade_variable == "prop_control_low" ~ "prop_control",
                                      TRUE ~ cascade_variable)) %>%
  select(countryGDPclass, wealth_quintile,cascade_variable,
         lower = value)

#shape upper bound to merge back in
upper <- data_n %>%
  select(countryGDPclass, wealth_quintile, 
         prop_aware_upp, 
         prop_tx_upp,
         prop_control_upp) %>%
  pivot_longer(prop_aware_upp:prop_control_upp, names_to = "cascade_variable") %>%
  mutate(cascade_variable = case_when(cascade_variable == "prop_aware_upp"  ~ "prop_aware",
                                      cascade_variable == "prop_tx_upp"  ~ "prop_tx",
                                      cascade_variable == "prop_control_upp" ~ "prop_control",
                                      TRUE ~ cascade_variable)) %>%
  select(countryGDPclass, wealth_quintile,cascade_variable,
         upper = value)

#join so have column with cascade variable names in each row and the upper and lower bound values next to it for ggplot format
cascade_q_data2 <- cascade_q_data %>% left_join(lower) %>% left_join(upper)

#factor cascade levels
cascade_q_data2$cascade_variable <- factor(cascade_q_data$cascade_variable, 
                                          levels = c("prop_aware", "prop_tx", "prop_control"))
cascade_q_data2$wealth_quintile <- as.factor(cascade_q_data$wealth_quintile)

#cascade_q_data2 <- cascade_q_data2 %>% 
 # left_join(gdp)

#cascade_q_data2$countryGDPclass <- factor(cascade_q_data2$countryGDPclass,
#                            levels = c("1","2", "3"),
#                            labels = c("Low-income", "Lower-middle Income", "Upper-middle Income"))

prop_htn2 <- cascade_q_data2 %>%
  group_by(wealth_quintile, countryGDPclass) %>%
 summarize(cascade_variable = "prop_htn",
         value = 100,
         lower = 100,
         upper = 100)

cascade_q_data3 <- cascade_q_data2 %>%
  rbind(prop_htn2) %>%
  arrange(cascade_variable, value)

cascade_q_data3$cascade_variable <- factor(cascade_q_data3$cascade_variable,
                                        levels = c("prop_htn","prop_aware","prop_tx", "prop_control"),
                                        labels = c("Hypertensives", "Aware", "Treated", "Controlled"))
cascade_q_data3$wealth_quintile <- factor(cascade_q_data3$wealth_quintile,
                                     levels = c("1", "2", "3", "4", "5"),
                                      labels= c("Q1", "Q2", "Q3", "Q4", "Q5"))

saveRDS(cascade_q_data3, "3 Output/cascade-graph-country-income-group.rds")
 
```

```{r bar graph cascades}

library(shades)
library(RColorBrewer)

cascade_country <- readRDS("3 Output/cascade-graph-country-income-group.rds")

# colors
blu_purp <- c("#8c96c6","#8c6bb1", "#88419d", "#810f7c", "#4d004b")
green <- c("#78c679", "#41ab5d", "#238443", "#005a32", "#004529")
purp_pink <- c("#f768a1", "#dd3497", "#ae017e", "#7a0177", "#49006a")
purple <- c("#9e9ac8", "#807dba", "#6a51a3", "#54278f", "#3f007d")
green_blu <- c("#67a9cf", "#3690c0", "#02818a", "#016c59", "#014636")

df <- cascade_country %>%
  filter(cascade_variable != "Hypertensives")

# Create a ggplot with 18 colors 
# Use scale_fill_manual
#ggplot(df) + 
#  geom_col(aes(name, Sepal.Length, fill = factor(Sepal.Length))) +
#  scale_fill_manual(values = mycolors) +
#  theme_minimal() +
#  theme(legend.position = "top")
# lines
ggplot(data = df, 
               aes(x = factor(cascade_variable),
                 #x = factor(cascade_variable), 
                    y = value,
                   #group = Country,
                    group = wealth_quintile, 
                    fill = wealth_quintile)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin = lower, ymax = upper,
                    group = wealth_quintile,
                    color = wealth_quintile),
                position = "dodge") +
  scale_y_continuous(labels = comma) +
  #scale_x_discrete(labels = c("Q1", "", "Treated", "Controlled"), expand = c(0.05,0.05)) +
  guides(fill=guide_legend(title="Wealth Quintile")) +
  labs(y = "People Living with Hypertension (%)", x = "",
       color = "Wealth Quintile") +
  #ggtitle("Cascades by Wealth Quintile and Country Income Group") +
  #theme_bw() +
  theme_minimal() +
  theme(aspect.ratio=40/40) +
  #facet_grid(rows = vars(countryGDPclass), cols = vars(wealth_quintile)) +
  facet_wrap(~countryGDPclass, nrow = 1, ncol = 3) +
  theme(legend.position = "bottom",
        panel.spacing.x = unit(3,"mm"),
        axis.text.x = element_text(angle = -40, size = 10),
        axis.text.y = element_text(size = 10),
        strip.text.y = element_text(size = 12),
        strip.text = element_text(size = 12)) +
  scale_fill_manual(values = green) +
  scale_color_manual(values = green) +
  ylim(0,100)

  ggsave("/Users/dorittalia/Desktop/Stephane HTN/Graphs/figure1-cascades-vars-Dec14.eps", width = 10, height = 5, dpi = 600)


```


# Figure 2

```{r}

difference <- readRDS("3 Output/difference-cvd-risk.rds") %>%
  mutate(scenario = case_when(scenario == "Baseline" ~ "Baseline",
                                scenario == "Scenario 1: Diagnosis" ~ "Diagnosis scenario",
                                scenario == "Scenario 2: Treatment" ~ "Treatment scenario"))

difference <- difference %>%
  group_by(country) %>%
  mutate(start = min(difference1_5),
         stop = max(difference1_5))

#difference$scenario <- factor(difference$scenario,
#                                     levels = c("Scenario 2: Treatment", "Scenario 1: Diagnosis", "Baseline"),
 #                                     labels= c("Treatment Scenario", "Diagnosis Scenario", "Baseline"))

graph_cvd2 <- difference %>%
  group_by(scenario) %>%
  arrange(difference1_5) 

oo <- graph_cvd2 %>%
  #filter(scenario == "Scenario 2: Treatment")
  filter(scenario == "Baseline")

o <- unique(oo$country)

#o1 <- graph_cvd2[(graph_cvd2$scenario == "Baseline"),] 
                  #& graph_cvd2$wealth_quintile == "Q1"),]

#graph_cvd2$country <- factor(graph_cvd2$country, levels = (o1$country))
graph_cvd2$country <- factor(graph_cvd2$country, levels = (o))

library(grid)
library(ggpubr)
text_high <- text_grob("\nHigher mean \nCVD risk in Q1", face = "italic", color="navy")
text_low <- text_grob("\nHigher mean \nCVD risk in Q5", face = "italic" ,color="navy")
text_mid <- text_grob("\nNo difference \nin CVD risk", face = "italic" ,color="navy")

#pdf("/Users/dorittalia/Desktop/Stephane HTN/Graphs/country-mean-cvd-points.pdf", width = 12, height = 10)
#test <- 
#reorder(country, mean)
ggplot(data = graph_cvd2, aes(x = difference1_5, 
                              y = country,
                              color = as.factor(scenario))) +
  geom_vline(xintercept = 0, color = "grey50", linetype = "longdash") + 
  geom_segment(aes(x=start ,xend=stop, y=country, yend=country, group = as.factor(scenario)), color="grey") +
    geom_point(size=2.5) + 
 geom_hline(yintercept = seq(1, length(graph_cvd2$country), by = 1), color="gray", size=.3, alpha=.1) + 
  theme_classic() +
  labs(x = "\n\n\nAbsolute (Percentage Point) Difference in Mean CVD Risk (Q1 - Q5)", color = "Scenario", y = "") +
  theme(legend.position = "right",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 11),
        axis.title.x = element_text(size = 12),
        legend.text = element_text(size = 12),
        strip.text = element_text(size = 13),
        legend.title = element_text(size = 14)) +
annotation_custom(text_high,xmin=8,xmax=8,ymin=-2,ymax=-2) + 
annotation_custom(text_low,xmin=-7.5,xmax=-7.5,ymin=-2,ymax=-2)+
  annotation_custom(text_mid,xmin=0,xmax=-0,ymin=-2,ymax=-2)+
coord_cartesian(clip="off")
#+
 #facet_wrap(~scenario) 
 #facet_grid(rows = vars(scenario), cols = vars(wealth_quintile))

ggsave("/Users/dorittalia/Desktop/Stephane HTN/Graphs/figure2-difference-q1-q5-v3.png", width = 12, height = 8)
ggsave("/Users/dorittalia/Desktop/Stephane HTN/Graphs/figure2-difference-q1-q5-v3.svg", width = 12, height = 8)

```

# Figure 3


```{r}

ggplot(data = abs_diff_total4, aes(x = wealth_quintile, y = averted_rate, fill = wealth_quintile, group = scenario)) +
  #geom_col(position = "dodge") +
  geom_bar(stat = "identity", position = position_stack(reverse = TRUE)) +
    geom_text(aes(label=round(averted_rate,1), nsmall = 1), vjust = 1.5, color = "white") +
  facet_grid(cols = vars(countryGDPclass), rows = vars(scenario)) +
  #facet_wrap(~scenario) +
  #scale_fill_manual(values = green_blu) +
  scale_fill_manual(values = blues) +
  #theme_bw() +
  theme_minimal() +
  #scale_fill_manual(values = c("#E5A825", "#832543", "#3D6879")) +
                    #,
                  #  labels = c("Diagnosed, Controlled Hypertension",
                   #            "Diagnosed, Uncontrolled Hypertension",
                   #            "Undiagnosed Hypertension")) +
  labs(x = "", y = "CVD cases averted per 1,000 people living with hypertension", fill = "Wealth Quintile") +
  theme(legend.position = "none") +
  #scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 13),
        strip.text = element_text(size = 14)) 


  ggsave("/Users/dorittalia/Desktop/Stephane HTN/Graphs/figure3-new-bars.eps", width = 10, height = 7)

```

# Figure 4


```{r}

ggplot(data = abs_diff_total3, aes(x = wealth_quintile, y = prop_cases*100, fill = wealth_quintile, group = scenario)) +
  #geom_col(position = "dodge") +
  geom_bar(stat = "identity", position = position_stack(reverse = TRUE)) +
    geom_text(aes(label=format(round(prop_cases*100,digits=1), nsmall = 1)), vjust = 1.5, color = "white") +
  facet_grid(cols = vars(countryGDPclass), rows = vars(scenario)) +
  #facet_wrap(~scenario) +
  #scale_fill_manual(values = purp_pink) +
  scale_fill_manual(values = purple) +
  #theme_bw() +
  theme_minimal() +
  #scale_fill_manual(values = c("#E5A825", "#832543", "#3D6879")) +
                    #,
                  #  labels = c("Diagnosed, Controlled Hypertension",
                   #            "Diagnosed, Uncontrolled Hypertension",
                   #            "Undiagnosed Hypertension")) +
  labs(x = "", y = "Percent (%) of total CVD cases averted", fill = "Wealth Quintile") +
  theme(legend.position = "none") +
  #scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 13),
        strip.text = element_text(size = 14)) 

ggsave("/Users/dorittalia/Desktop/Stephane HTN/Graphs/total-prop-lmic-fig4-purp.eps", width = 10, height = 7, dpi = 600)
```


# Figure 5

```{r}

library(ggbeeswarm)
ggplot(data = abs, 
               aes(x = wealth_quintile, 
                          y = mean,
                   color = countryGDPclass)) +
                   #color = country)) +
                   #label = plot_label)) +
  ggbeeswarm::geom_beeswarm(cex = 2, method = "square",corral = "wrap", coral.width = 1, alpha = 0.8) +
  #geom_jitter(position=position_jitter(width=0.1), alpha = 0.7) +
  #geom_text(position = position_jitter(seed = 1), size = 2) +
  geom_smooth(aes(group = auc_gap_rank), fill="grey75", alpha=0.3, 
              linetype="solid", color = "darkblue",
              se=T, formula = y ~ x, method = "lm", size=0.5, fullrange=T) +
              #method = "loess", 
  scale_y_continuous(labels = comma) +
  guides(color=guide_legend(title="Country income group")) +
  labs(y = "Mean CVD Cases Averted per 1,000 People Living with Hypertension", x = "Weath Quintile") +
 # theme_bw() +
  theme_minimal() +
  theme(legend.position = "bottom",
        strip.text = element_text(size = 12),
        axis.title.y = element_text(size=10)) +
  facet_grid(cols = vars(auc_gap_rank), rows = vars(scenario)) +
  ylim(0,55) +
  scale_color_brewer(palette = "Dark2")

ggsave("/Users/dorittalia/Desktop/Stephane HTN/Graphs/figure5-byauc-2.jpg", height =6, width=9,dpi = 600)

```






