---
title: "Education Appendix Results"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(data.table)
library(ggplot2)
```

Appendix Figure XX. Mean proportion of people living with hypertension aware of their diagnosis, on treatment, and with controlled blood pressure by education category across low-income, lower-middle income, and upper-middle income country groups.

```{r}
cascade_edu_long <- fread("~/Documents/Stanford/Projects/CVD SES/output/figures/figure1_education_data.csv")

cascade_edu_long$educat <- factor(cascade_edu_long$educat,
                       levels = c("No formal schooling", "Less than primary school", "Primary school completed", "Some high school", "High school or above"))
cascade_edu_long$variable <- factor(cascade_edu_long$variable, 
                                    levels = c("mean_htn", "mean_aware", "mean_treated", "mean_controlled"))

ggplot(data = cascade_edu_long, aes(x = variable, y = value, color = educat, group = educat)) + geom_point() +
  geom_line() +
  facet_wrap(~countryGDPclass) +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = c("", "Aware", "Treated", "Controlled")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1), legend.position = "bottom",
        strip.background = element_rect(fill = "NA")) +
  labs(y = "People Living with Hypertension", 
       x = "", color = "Education Category") +
  guides(color = guide_legend(nrow=2, byrow = TRUE))

```

Appendix Figure XX. Mean difference in cardiovascular disease cases per 1,000 people living with hypertension across education categories, modelled scenarios (either “Diagnosis” (Scenario 1) or “Treatment” (Scenario 2)) and country-level income group.

```{r}
scenarios <- fread("~/Documents/Stanford/Projects/CVD SES/output/figures/figure4_education_data.csv")
scenarios$educat <- factor(scenarios$educat,
                       levels = c("No formal schooling", "Less than primary school", "Primary school completed", "Some high school", "High school or above"))

ggplot(data = scenarios, aes(x = educat, y = cases_averted)) + geom_point(aes(color = Country), alpha = .8) + 
  geom_smooth(aes(x = as.numeric(educat), y = cases_averted), method = "lm", size = .4, alpha = .1, color = "maroon", fill = "maroon") +
  facet_grid(scenario~countryGDPclass) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "", y = "Mean Difference in CVD Cases per 1,000\nPeople Living with Hypertension") +
  theme(axis.text.x = element_text(angle = 70, hjust = 1))

```